




# Old

## Peaceful Equilibrium {id="br"}

\begin{equation*}
\begin{split}
\max_{ \tilde{\bm{\tau}}_i } & \quad G_i \left( h( \tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i} ) \right) \\
\text{subject to} & \quad \underbrace{\tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) G_j \left( h( \bm{1}_i; \tilde{\bm{\tau}}_{-i} ); v_j \right) + \left( 1 - \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \right) G_j \left( h (\tilde{\bm{\tau}} ); v_j \right) - c_j \geq 0}_{\text{war constraint}} \quad \text{for all } j 
\end{split}
\end{equation*}

## Peaceful Equilibrium

\begin{equation*}
\begin{split}
\max_{ \tilde{\bm{\tau}}_i } & \quad G_i \left( h( \tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i} ) \right) \\
\text{subject to} & \quad \color{bcOrange} \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \color{black} G_j \left( h( \bm{1}_i; \tilde{\bm{\tau}}_{-i} ); v_j \right) + \left( 1 - \color{bcOrange} \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \color{black} \right) G_j \left( h (\tilde{\bm{\tau}} ); v_j \right) - c_j \geq 0 \quad \text{for all } j
\end{split}
\end{equation*}

**Contest Function**

$$
\color{bcOrange} \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \color{black} = \frac{ \rho_{ji}(\bm{W}; \bm{\alpha}) M_j }{ \rho_{ji}(\bm{W}; \bm{\alpha}) M_j + M_i }
$$

- $\rho_{ji}(\bm{W}; \bm{\alpha})$ loss of strength gradient
- $M_i$ military strength

## Peaceful Equilibrium

\begin{equation*}
\begin{split}
\max_{ \tilde{\bm{\tau}}_i } & \quad G_i \left( h( \tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i} ) \right) \\
\text{subject to} & \quad \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \color{bcOrange} G_j \left( h( \bm{1}_i; \tilde{\bm{\tau}}_{-i} ); v_j \right) \color{black} + \left( 1 - \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \right) G_j \left( h (\tilde{\bm{\tau}} ); v_j \right) - c_j \geq 0 \quad \text{for all } j
\end{split}
\end{equation*}

**Contest Function**

$$
\tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) = \frac{ \rho_{ji}(\bm{W}; \bm{\alpha}) M_j }{ \rho_{ji}(\bm{W}; \bm{\alpha}) M_j + M_i }
$$

- $\rho_{ji}(\bm{W}; \bm{\alpha})$ loss of strength gradient
- $M_i$ military strength

**Conquest Values**

$$
\color{bcOrange} G_j \left( h( \bm{1}_i; \tilde{\bm{\tau}}_{-i} ); v_j \right)
$$

## Peaceful Equilibrium

\begin{equation*}
\begin{split}
\max_{ \tilde{\bm{\tau}}_i } & \quad G_i \left( h( \tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i} ) \right) \\
\text{subject to} & \quad \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) G_j \left( h( \bm{1}_i; \tilde{\bm{\tau}}_{-i} ); v_j \right) + \left( 1 - \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \right) G_j \left( h (\tilde{\bm{\tau}} ); v_j \right) - c_j \geq 0 \quad \text{for all } j
\end{split}
\end{equation*}

**Contest Function**

$$
\tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) = \frac{ \rho_{ji}(\bm{W}; \bm{\alpha}) M_j }{ \rho_{ji}(\bm{W}; \bm{\alpha}) M_j + M_i }
$$

- $\rho_{ji}(\bm{W}; \bm{\alpha})$ loss of strength gradient
- $M_i$ military strength

**Conquest Values**

$$
G_j \left( h( \bm{1}_i; \tilde{\bm{\tau}}_{-i} ); v_j \right)
$$

**Equilibrium**

$$
\bm{\tau}^\star(\color{bcOrange} \bm{\theta} \color{black})
$$

- $\color{bcOrange} \bm{\theta} \color{black}$ - estimand

## Estimation {id="estimation"}

**Data**

- $\tau_{ij}$ - aggregate policy barrier to trade imposed by country $i$ on goods from country $j$
  + Measurement: @Cooley2019b

**Measurement Error**

$$
\tau_{ij} = \tau_{ij}^\star(\bm{\theta}) + \epsilon_{ij}
$$

**Mathematical Program with Equilibrium Constraints [@Su2012]**

\begin{equation*}
\begin{split}
\min_{\bm{\theta}, \bm{\tau}^\star} & \quad \sum_i \sum_j \left( \epsilon_{ij}(\bm{\theta}) \right)^2 \\
\text{subject to} & \quad \color{bcOrange} \nabla_{\bm{\tau}_i} \mathcal{L}_i(\bm{\theta}) \color{black} = 0 \quad \text{for all } i
\end{split}
\end{equation*}

- $\color{bcOrange} \nabla_{\bm{\tau}_i} \mathcal{L}_i(\bm{\theta})$ - gradient of Lagrangian

. . . 

**Estimates**

$$
\hat{\bm{\theta}} = \left( \hat{\bm{v}}, \hat{\bm{\alpha}}, \hat{c} \right)
$$

- $\hat{\bm{v}}$ preference for protectionism
- $\hat{\bm{\alpha}}$ loss of military strength over geographic distance
- $\hat{c}$ (relative) costs of war

## Results {id="results"}

**Dyadic War Cost-Benefit Ratios**

```{r cb_ratio, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

# source("02_figs/cbratio.R")
# cb_ratio_plot + theme(aspect.ratio=1)

```











## Thank You {.aligncenter}

[brendancooley.com](http://brendancooley.com)

[bcooley@princeton.edu](mailto:bcooley@princeton.edu)

















## Policy Problem in Changes {id="policyHats"}

**Government Welfare**

$$
\hat{G}_i(\hat{\bm{\tau}}; v_i) = \hat{V}_i \left( \hat{h}(\hat{\bm{\tau}}) \right) \hat{r}_i \left(\hat{h}(\hat{\bm{\tau}}); v_i \right)
$$

**Constrained Policy Problem in Changes**

\begin{equation*}
\begin{split}
\max_{ \hat{\tilde{\bm{\tau}}}_i } & \quad \hat{G}_i(\hat{\tilde{\bm{\tau}}}_i; \hat{\tilde{\bm{\tau}}}_{-i}) \\
\text{subject to} & \quad \hat{G}_j(\hat{\tilde{\bm{\tau}}}) - \hat{G}_j(\bm{1}_i; \hat{\tilde{\bm{\tau}}}_{-i}) + \hat{c} \left( \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \right)^{-1} \geq 0 \quad \text{for all } j \neq i
\end{split}
\end{equation*}

<a href="#/toc" style="float: right;">Back</a>

## Multilateral Contest Function {id="multilateralcontest"}

$$
\chi_{ij}(\bm{a}, \bm{m}) = \frac{ a_{ij} \rho_{ij}(\bm{W}; \bm{\alpha}) M_i }{ \sum_k a_{kj} \rho_{kj}(\bm{W}; \bm{\alpha}) M_k }
$$

<a href="#/toc" style="float: right;">Back</a>

## Military Expenditure {id="milex"}

```{r milex, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center", fig.height=5}

# source("02_figs/milex.R")
# milexFig + theme(aspect.ratio=1)

```

<a href="#/toc" style="float: right;">Back</a>

## Protectionism Estimates {id="v_est"}


```{r v_estsT, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

# source("02_figs/ccodes.R")

# kable(v_estsT, booktabs = T, caption = "Preference Parameter ($\\tilde{\\bm{v}}$) Estimates", escape = FALSE) %>% kable_styling(position = "center")

```

<a href="#/toc" style="float: right;">Back</a>

## Conquest Values {id="rcv"}

**Conquest Values**

$$
G_j \left( h(\bm{1}_i ; \tilde{\bm{\tau}}_{-i});v_j \right)
$$

```{r rcv, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

# source("02_figs/rcv.R")
# rcvhm(rcv_eq, mint, maxt)

```

<a href="#/toc" style="float: right;">Back</a>

## Probability of Successful Conquest {id="chi_est"}

```{r chi, echo=FALSE, warning=FALSE, message=FALSE,  fig.align="center"}

# source("02_figs/chi.R")
# chihm(chi, minchi, maxchi)

```
<a href="#/toc" style="float: right;">Back</a>


<!-- hide references -->
<hr style="height:30em; visibility:hidden;" />