---
title: | 
	| Trade Policy in the Shadow of Power
	| \tiny \hfill
    | \Large Quantifying Military Coercion in the International System
author:
	- name: Brendan Cooley
      affiliation: Ph.D. Candidate, Department of Politics, Princeton University
date: \today
abstract: In international relations, how does latent military coercion affect governments’ policy choices? Because militarily powerful governments can credibly threaten to impose their policy preferences by force, weaker governments may adjust their policy choices to avoid costly conflict. This setting raises an inference problem -- do observed policies reflect the preferences of the governmnets that adopted them or the military constraints of the anarchic international system? Here, I investigate the role of this “shadow of power” in determining trade policy. Specifically, I build a model of trade policy choice under threat that allows me to measure empirically governments’ underlying trade policy preferences and the magnitude of policy appeasement attributable to latent military coercion. Once estimated, the model can be used to conduct counterfactual experiments – such as assessing the international economic effects of Chinese military growth or the military strategic effects of Chinese political liberalization. These and other exercises shed light on how military power affects international economic exchange, and how expectations about exchange affect governments’ military strategies.
thanks: Thanks go here.
# jelcodes: JEL codes go here

bibliography: /Users/bcooley/Dropbox (Princeton)/References/library.bib
biblio-style: apsr

papersize: letter
documentclass: article
geometry: margin=1.25in
link-citations: true

output:
	fig_caption: yes
    citation_package: natbib

---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

helperPath <- "~/Dropbox (Princeton)/14_Software/R/"
helperFiles <- list.files(helperPath)
for (i in helperFiles) {
  source(paste0(helperPath, i))
}

libs <- c("knitr", "tidyverse", "countrycode", "kableExtra", "latex2exp", "patchwork")
ipak(libs)

# not available
AwarEntry <- "NA"
DGammac <- "NA"
Pc <- "NA"
Pm <- "NA"
Aeconomy <- "NA"
AeconomyC <- "NA"
Achat <- "NA"
# Aproofs <- "NA"
Aalphagamma <- "NA"
Ampec <- "NA"
AestimationAlg <- "NA"

# load references picked up later in document
if (file.exists('references.RData')) load('references.RData')

# setup definition, assumption, proposition, lemma tickers
Dtick <- 1
Atick <- 1
Ptick <- 1
Ltick <- 1

tpspPath <- "~/Dropbox (Princeton)/1_Papers/tpsp/01_data/"
dataPath <- paste0(tpspPath, "tpsp_data_mini/")
resultsPath <- paste0(tpspPath, "results_mini/")
estimatesPath <- paste0(resultsPath, "estimates/")

# economic parameters 
theta <- read_csv(paste0(dataPath, "theta.csv"), col_names=FALSE) %>% pull(.)
beta <- read_csv(paste0(dataPath, "beta.csv"), col_names=FALSE) %>% pull(.)
ccodes <- read_csv(paste0(dataPath, "ccodes.csv"), col_names=FALSE)
y <- read_csv(paste0(dataPath, "y.csv"), col_names=FALSE)
Y <- read_csv(paste0(dataPath, "year.csv"), col_names=FALSE) %>% pull(.)
N <- length(ccodes %>% pull(.))

# data
tauM <- read_csv(paste0(dataPath, "tau.csv"), col_names=FALSE) %>% as.matrix()
tau <- read_csv(paste0(dataPath, "tau.csv"), col_names=FALSE)
milex <- read_csv(paste0(dataPath, "milex.csv"), col_names=FALSE)
rcv <- read_csv(paste0(resultsPath, "rcv.csv"), col_names=FALSE)
b_vals <- read_csv(paste0(resultsPath, "b_vals.csv"), col_names=FALSE)
W <- read_csv(paste0(dataPath, "cDists.csv"), col_names=FALSE)
W <- log(W)

# estimates
b_tilde <- read_csv(paste0(resultsPath, "b_tilde.csv"), col_names=FALSE)
gamma_tilde <- read_csv(paste0(resultsPath, "gamma_tilde.csv"), col_names=FALSE) %>% pull(.)
alpha_tilde <- read_csv(paste0(resultsPath, "alpha_tilde.csv"), col_names=FALSE) %>% pull(.)
c_hat_tilde <- read_csv(paste0(resultsPath, "c_hat_tilde.csv"), col_names=FALSE) %>% pull(.)
simga_epsilon_tilde <- read_csv(paste0(resultsPath, "sigma_epsilon_tilde.csv"), col_names=FALSE) %>% pull(.)

# results
# Ghatft <- read_csv(paste0(resultsPath, "Ghatft.csv"), col_names=FALSE)
# rcv0 <- read_csv(paste0(resultsPath, "rcv0.csv"), col_names=FALSE)
# rcv1 <- read_csv(paste0(resultsPath, "rcv1.csv"), col_names=FALSE)

```

\newpage

# Introduction

```{r, child = "sections/introduction.rmd"}
```


## Literature

```{r, child = "sections/literature.md"}
```

# Model

```{r, child = "sections/model.md"}
```

# Data and Calibration of Economy

```{r, child = "sections/data.rmd"}
```

# Estimation

```{r, child = "sections/estimation.md"}
```

# Results

```{r, child = "sections/results.rmd"}
```

# Counterfactual: From Anarchy to Pacifism

```{r, child = "sections/counterfactual.rmd"}
```

# Conclusion

```{r, child = "sections/conclusion.md"}
```


\clearpage

# Appendix

```{r Appendix Numbering, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

a <- 1

# reset definition, assumption, proposition, lemma tickers
Dtick <- 1
Atick <- 1
Ptick <- 1
Ltick <- 1

Aeconomy <- LETTERS[a]
```

## `r Aeconomy`: Economy

```{r, child = "sections/Aeconomy.md"}
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

a <- a + 1

# reset definition, assumption, proposition, lemma tickers
Dtick <- 1
Atick <- 1
Ptick <- 1
Ltick <- 1

AeconomyC <- LETTERS[a]

```

## `r AeconomyC`: Calibration of Economy

```{r, child = "sections/AeconomyC.rmd"}
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

a <- a + 1

# reset definition, assumption, proposition, lemma tickers
Dtick <- 1
Atick <- 1
Ptick <- 1
Ltick <- 1

AwarEntry <- LETTERS[a]

```

## `r AwarEntry`: War Entry

```{r, child = "sections/AwarEntry.md"}
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

a <- a + 1

Ampec <- LETTERS[a]

```

## `r Ampec`: Best Responses as Mathematical Programs with Equilibrium Constraints

```{r, child = "sections/Ampec.md"}
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

a <- a + 1

Aalphagamma <- LETTERS[a]

```

## `r Aalphagamma`: Estimation of $\gamma$ and $\bm{\alpha}$

```{r, child = "sections/Aalphagamma.md"}
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

a <- a + 1

AestimationAlg <- LETTERS[a]

```

## `r AestimationAlg`: Estimation Algorithm

```{r, child = "sections/AestimationAlg.md"}
```

\clearpage

# References

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

save.image('references.RData')

```