---
title: "Trade Policy in the Shadow of Power"
subtitle: "Quantifying Military Coercion in the International System"
date: "1 September 2019"
author: Brendan Cooley
position: Ph.D. Candidate
institution: Princeton University
email: "bcooley (at) princeton.edu"

bibliography: /Users/brendancooley/Dropbox (Princeton)/References/library.bib
biblio-style: apsr

backgroundTitle: "figs/cover.jpg"

output:
  revealjs::revealjs_presentation:
    template: "css/cooley-reveal.html"
    css: "css/cooley-reveal.css"
    backgroundTransition: none
    transition: none
    self_contained: false
    # reveal_plugins: ["notes"]
    lib_dir: index_files
    reveal_options:
      slideNumber: false
      progress: false
      controls: false      
    includes:
      after_body: "css/plugins.html"
---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

helperPath <- "~/Dropbox (Princeton)/14_Software/R/"
helperFiles <- list.files(helperPath)
for (i in helperFiles) {
  source(paste0(helperPath, i))
}

libs <- c("tidyverse", "patchwork", "countrycode", "knitr", "kableExtra")
ipak(libs)

analysisPath <- "working/analysis/"
dataPath <- paste0(analysisPath, "tpsp_data/")
resultsPath <- paste0(analysisPath, "results/")

# data
ccodes <- read_csv(paste0(dataPath, "ccodes.csv"), col_names=FALSE)
Y <- read_csv(paste0(dataPath, "year.csv"), col_names=FALSE) %>% pull(.)
tau <- read_csv(paste0(dataPath, "tau.csv"), col_names=FALSE)

# results
Ghatft <- read_csv(paste0(resultsPath, "Ghatft.csv"), col_names=FALSE)
rcv0 <- read_csv(paste0(resultsPath, "rcv0.csv"), col_names=FALSE)
rcv1 <- read_csv(paste0(resultsPath, "rcv1.csv"), col_names=FALSE)

# references from paper
if (file.exists('references.RData')) load('references.RData')

```

## Power and Preferences {id="introduction"}

**Anarchy and Inference**

- Anarchy $\implies$ powerful governments can impose policies on others by force
- Bargaining critique: policies reflect shadow of power
  + @Brito1985, @Fearon1995, @Art1996
- **Question:** Do observed policies reflect **preferences** of the governments that adopted them or **constraints of anarchy?**

. . . 

**Trade Policy: What Do Governments Want?**

- **Heterogeneity** in desired protectionism
  + @Grossman1994, @Gawande2009
- Mercantilism induces **conflicts of interest** between governments
  + Gunboat diplomacy: powerful impose openness abroad [@Findlay2007]

. . . 

**Trade Policy: Does It Matter?**

- Tariffs small, aggregate policy-induced trade frictions large
  + ~order of magnitude larger than tariffs [@Cooley2019b] (<a href="#/barriers">barriers</a>)
- Welfare effects of trade frictions
  + @Autor2013, @Costinot2015, @Goldberg2016

## Anarchy and Inference: Approach {id="approach"}

**Ideal Experiment**

- Exogenously manipulate governments' military capacity
- Attribute changes in trade policy to latent effect of military coercion

. . . 

**A Coercive International Political Economy**

$$
\left\{ \bm{\theta}, \bm{M} \right\} \rightarrow \bm{\tau}
$$

- $\bm{\theta}$ -- structural parameters (power and preferences)
- $\bm{M}$ -- governments' military endowment (expenditure)
- $\bm{\tau}$ -- governments' trade policies

. . . 

**Estimation:** $\left\{ \bm{\tau}, \bm{M} \right\} \rightarrow \bm{\theta}$

. . . 

**Counterfactuals:** $\left\{ \bm{\theta}^\prime, \bm{M}^\prime \right\} \rightarrow \bm{\tau}^\prime$

- Shadow of power
  + Effect of changing military endowments on trade policy
- Liberal/commercial peace
  + Effect of changing preferences for openness on military strategies

## Agenda {.centercontent}

1. Model
2. Preliminary Results
3. Identification

## Model {.aligncenter}

$$
\left\{ \bm{\theta}, \bm{M} \right\} \rightarrow \bm{\tau}
$$

## Coercive International Political Economy {id="cipe"}

- Governments indexed $i \in \left\{ 1, ..., N \right\}$

. . . 

**Sequence**

1. ($\Gamma^{\bm{m}}$) Governments set military strategies
    + allocations of effort over potential wars
2. ($\Gamma^{\bm{\tau}}$) Governments make trade policy announcements
3. ($\Gamma^{\bm{a}}$) Wars
    + Winners choose trade policies for vanquished governments
4. ($h(\bm{\tau})$) Economic (general equilibrium) consequences of trade policies

. . . 

**Payoffs**

$$
G_i \left( h(\bm{\tau}), \bm{a} \right)
$$

## ($h(\bm{\tau})$) Economy {id="economy"}

$$
\bm{\tau} = \begin{pmatrix}
\tau_{11} & \cdots & \cdots & \cdots & \tau_{1N} \\
\vdots & \ddots & \vdots & \iddots & \vdots \\
\vdots & \cdots & \tau_{ij} & \cdots & \vdots \\
\vdots & \iddots & \vdots & \ddots & \vdots \\
\tau_{N1} & \cdots & \cdots & \cdots & \tau_{NN}
\end{pmatrix}
$$

## ($h(\bm{\tau})$) Economy

$$
\bm{\tau} = \begin{pmatrix}
\tau_{11} & \cdots & \cdots & \cdots & \tau_{1N} \\
\vdots & \ddots & \vdots & \iddots & \vdots \\
\vdots & \cdots & \color{bcOrange} \tau_{ij} & \cdots & \vdots \\
\vdots & \iddots & \vdots & \ddots & \vdots \\
\tau_{N1} & \cdots & \cdots & \cdots & \tau_{NN}
\end{pmatrix}
$$

<hr style="height:2em; visibility:hidden;" />

- $\color{bcOrange} \tau_{ij}$: trade barrier government $i$ imposes on imports from $j$
- $\color{bcOrange} \tau_{ij} \color{black} - 1$: ad-valorem tariff equivalent
- $\tau_{ij} = 1 \implies$ free trade
- $\tau_{ii} = 1$ for all $i$

## ($h(\bm{\tau})$) Economy

$$
\bm{\tau} = \begin{pmatrix}
\color{bcOrange} \tau_{11} & \color{bcOrange} \cdots & \color{bcOrange} \cdots & \color{bcOrange} \cdots & \color{bcOrange} \tau_{1N} \\
\vdots & \ddots & \vdots & \iddots & \vdots \\
\vdots & \cdots & \tau_{ij} & \cdots & \vdots \\
\vdots & \iddots & \vdots & \ddots & \vdots \\
\tau_{N1} & \cdots & \cdots & \cdots & \tau_{NN}
\end{pmatrix}
$$

<hr style="height:2em; visibility:hidden;" />

$$
\color{bcOrange} \bm{\tau}_1 = \begin{pmatrix} \tau_{11} & \cdots & \cdots & \cdots & \tau_{1N}
\end{pmatrix}
$$

<hr style="height:2em; visibility:hidden;" />

- Government 1's trade policy

## ($h(\bm{\tau})$) Economy

```{r tauhm1, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

source("figs/tau.R")
tauhm(tau)

```

## ($h(\bm{\tau})$) Economy

```{r tauhm2, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

source("figs/tau.R")
tauhm(tau, highlight="USA")

```

## ($h(\bm{\tau})$) Economy

$$
\color{bcOrange} \bm{\tau} \color{black} = \begin{pmatrix}
\tau_{11} & \cdots & \cdots & \cdots & \tau_{1N} \\
\vdots & \ddots & \vdots & \iddots & \vdots \\
\vdots & \cdots & \tau_{ij} & \cdots & \vdots \\
\vdots & \iddots & \vdots & \ddots & \vdots \\
\tau_{N1} & \cdots & \cdots & \cdots & \tau_{NN}
\end{pmatrix}
$$

<hr style="height:2em; visibility:hidden;" />

$$
\color{bcOrange} h(\bm{\tau}) \rightarrow \begin{pmatrix}
w_1 \\
\vdots \\
w_N
\end{pmatrix} = \bm{w}
$$

## ($h(\bm{\tau})$) Economy

$$
h(\bm{\tau}) \rightarrow \begin{pmatrix}
w_1 \\
\vdots \\
w_N
\end{pmatrix} = \color{bcOrange} \bm{w}
$$

. . . 

<hr style="height:1em; visibility:hidden;" />

- $V_i( \color{bcOrange} \bm{w} \color{black})$: welfare of representative consumer in $i$
- $X_{ij}(\color{bcOrange} \bm{w} \color{black})$: $i$'s imports of goods from $j$
- Rents (tariff revenue):

$$
r_i(\color{bcOrange} \bm{w} \color{black}) = \sum_j (\tau_{ij} - 1) X_{ij}(\color{bcOrange} \bm{w} \color{black})
$$

. . . 

**Government Objective**

$$
G_i = V_i( \color{bcOrange} \bm{w} \color{black})^{1 - b_i} r_i(\color{bcOrange} \bm{w} \color{black})^{b_i}
$$

## ($h(\bm{\tau})$) Economy {id="economyLast"}

$$
h(\bm{\tau}) \rightarrow \begin{pmatrix}
w_1 \\
\vdots \\
w_N
\end{pmatrix} = \bm{w}
$$

<hr style="height:1em; visibility:hidden;" />

- $V_i(\bm{w})$: welfare of representative consumer in $i$
- $X_{ij}(\bm{w})$: $i$'s imports of goods from $j$
- Rents (tariff revenue):

$$
r_i(\bm{w} \color{black}) = \sum_j (\tau_{ij} - 1) X_{ij}(\bm{w})
$$

**Government Objective**

$$
G_i = V_i(\bm{w})^{ \color{bcOrange} 1 - b_i \color{black} } r_i(\bm{w})^{\color{bcOrange} b_i \color{black} }
$$

. . . 

- $\color{bcOrange} b_i = 0$: government maximizes consumer welfare
- $\color{bcOrange} b_i = 1$: government maximizes rents
- <a href="#/freetrade">Free Trade Counterfactual</a>

## ($\Gamma^{\bm{a}}$) Wars {id="wars"}

**Optimal Post-Conquest Policies**

$$
\bm{\tau}_j^{i \star} = \argmax_{\bm{\tau}_j} \quad G_i(\bm{\tau}_j ; \tilde{\bm{\tau}}_{-j})
$$

## ($\Gamma^{\bm{a}}$) Wars

**Optimal Post-Conquest Policies**

$$
\color{bcOrange} \bm{\tau}_j^{i \star} \color{black} = \argmax_{\bm{\tau}_j} \quad G_{\color{bcOrange} i} \color{black} (\bm{\tau}_{\color{bcOrange} j} \color{black} ; \tilde{\bm{\tau}}_{-j})
$$

- $\color{bcOrange} \bm{\tau}_j^{i \star}$: trade policies in $\color{bcOrange} j$ imposed by government $\color{bcOrange} i$ post-conquest

## ($\Gamma^{\bm{a}}$) Wars {id="wars_rcv"}

**Optimal Post-Conquest Policies**

$$
\color{bcOrange} \bm{\tau}_j^{i \star} \color{black} = \argmax_{\bm{\tau}_j} \quad G_{i}(\bm{\tau}_{j}; \tilde{\bm{\tau}}_{-j})
$$

- $\color{bcOrange} \bm{\tau}_j^{i \star}$: trade policies in $j$ imposed by government $i$ post-conquest

**Conquest Values**

$$
G_i(\color{bcOrange} \bm{\tau}_j^{i \star} \color{black} ; \tilde{\bm{\tau}}_{-j})
$$

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_j(\bm{\tau}_i^{j \star} \color{black} ; \tilde{\bm{\tau}}_{-i})
$$

```{r rcv1, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

source("figs/rcv.R")
rcvhm(rcv0, 0, mint, maxt) + plot_spacer()

```

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_j(\bm{\tau}_i^{j \star} \color{black} ; \tilde{\bm{\tau}}_{-i})
$$

```{r rcv2, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

source("figs/rcv.R")
rcvhm(rcv0, 0, mint, maxt) + rcvhm(rcv1, 1, mint, maxt)

```

## ($\Gamma^{\bm{a}}$) Wars {id="contest"}

**Conquest Values**

$$
G_j(\bm{\tau}_i^{j \star} \color{black} ; \tilde{\bm{\tau}}_{-i})
$$

. . . 

**Contest Function (Dyadic)** (<a href="#/multilateralcontest">Multilateral Version</a>)

$$
\chi_{ji}(\bm{m}) = \frac{ \rho_{ji}(\bm{W}; \bm{\alpha}) m_{ji} }{ \rho_{ji}(\bm{W}; \bm{\alpha}) m_{ji} + m_{ii} }
$$

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_j(\bm{\tau}_i^{j \star} \color{black} ; \tilde{\bm{\tau}}_{-i})
$$

**Contest Function (Dyadic)**

$$
\color{bcOrange} \chi_{ji}(\bm{m}) \color{black} = \frac{ \rho_{ji}(\bm{W}; \bm{\alpha}) m_{ji} }{ \rho_{ji}(\bm{W}; \bm{\alpha}) m_{ji} + m_{ii} }
$$

- $\color{bcOrange} \chi_{ji}$: probability $\color{bcOrange} j$ successfully conquers $\color{bcOrange} i$

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_j(\bm{\tau}_i^{j \star} \color{black} ; \tilde{\bm{\tau}}_{-i})
$$

**Contest Function (Dyadic)**

$$
\chi_{ji}( \color{bcOrange} \bm{m} \color{black}) = \frac{ \rho_{ji}(\bm{W}; \bm{\alpha}) \color{bcOrange} m_{ji} \color{black} }{ \rho_{ji}(\bm{W}; \bm{\alpha}) \color{bcOrange} m_{ji} \color{black} + \color{bcOrange} m_{ii} \color{black} }
$$

- $\chi_{ji}$: probability $j$ successfully conquers $i$
- $\color{bcOrange} \bm{m}$: military effort
- $\color{bcOrange} m_{ji}$: effort $j$ dedicates toward threatening $i$
- $\color{bcOrange} m_{ii}$: effort $i$ dedicates toward self-defense

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_j(\bm{\tau}_i^{j \star} \color{black} ; \tilde{\bm{\tau}}_{-i})
$$

**Contest Function (Dyadic)**

$$
\chi_{ji}(\bm{m}) = \frac{ \color{bcOrange} \rho_{ji} \color{black} (\bm{W}; \bm{\alpha}) m_{ji} }{ \color{bcOrange} \rho_{ji} \color{black} (\bm{W}; \bm{\alpha}) m_{ji} + m_{ii} }
$$

- $\chi_{ji}$: probability $j$ successfully conquers $i$
- $\bm{m}$: military effort
- $m_{ji}$: effort $j$ dedicates toward threatening $i$
- $m_{ii}$: effort $i$ dedicates toward self-defense
- $\color{bcOrange} \rho_{ji} \color{black} \in [0, 1]$: loss of strength gradient

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_j(\bm{\tau}_i^{j \star} \color{black} ; \tilde{\bm{\tau}}_{-i})
$$

**Contest Function (Dyadic)**

$$
\chi_{ji}(\bm{m}) = \frac{ \rho_{ji} (\color{bcOrange} \bm{W} \color{black} ; \bm{\alpha}) m_{ji} }{ \rho_{ji} ( \color{bcOrange} \bm{W} \color{black} ; \bm{\alpha}) m_{ji} + m_{ii} }
$$

- $\chi_{ji}$: probability $j$ successfully conquers $i$
- $\bm{m}$: military effort
- $m_{ji}$: effort $j$ dedicates toward threatening $i$
- $m_{ii}$: effort $i$ dedicates toward self-defense
- $\rho_{ji} \in [0, 1]$: loss of strength gradient
- $\color{bcOrange} \bm{W}$: dyadic geography

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_j(\bm{\tau}_i^{j \star} \color{black} ; \tilde{\bm{\tau}}_{-j})
$$

**Contest Function (Dyadic)**

$$
\chi_{ji}(\bm{m}) = \frac{ \rho_{ji} (\bm{W}; \color{bcOrange} \bm{\alpha} \color{black}) m_{ji} }{ \rho_{ji} ( \bm{W}; \color{bcOrange} \bm{\alpha} \color{black}) m_{ji} + m_{ii} }
$$

- $\chi_{ji}$: probability $j$ successfully conquers $i$
- $\bm{m}$: military effort
- $m_{ji}$: effort $j$ dedicates toward threatening $i$
- $m_{ii}$: effort $i$ dedicates toward self-defense
- $\rho_{ji} \in [0, 1]$: loss of strength gradient
- $\bm{W}$: dyadic geography
- $\color{bcOrange} \bm{\alpha}$: structural parameters

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_j(\bm{\tau}_i^{j \star} \color{black} ; \tilde{\bm{\tau}}_{-j})
$$

**Contest Function (Dyadic)**

$$
\color{bcOrange} \chi_{ji} (\bm{m}) \color{black} = \frac{ \rho_{ji} (\bm{W}; \bm{\alpha}) m_{ji} }{ \rho_{ji} (\bm{W}; \bm{\alpha}) m_{ji} + m_{ii} }
$$

**Reservation Values**

$$
\color{bcOrange} \chi_{ji} (\bm{m}) \color{black} G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \color{bcOrange}  \left( 1 - \chi_{ji} (\bm{m}) \right) \color{black} G_j(\tilde{\bm{\tau}}) - c_j
$$

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_j(\bm{\tau}_i^{j \star} \color{black} ; \tilde{\bm{\tau}}_{-i})
$$

**Contest Function (Dyadic)**

$$
\chi_{ji} (\bm{m}) = \frac{ \rho_{ji} (\bm{W}; \bm{\alpha}) m_{ji} }{ \rho_{ji} (\bm{W}; \bm{\alpha}) m_{ji} + m_{ii} }
$$

**Reservation Values**

$$
\chi_{ji} (\bm{m}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\bm{m}) \right) G_j(\tilde{\bm{\tau}}) - \color{bcOrange} c_j
$$

- $\color{bcOrange} c_j$: war cost

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_j(\bm{\tau}_i^{j \star} \color{black} ; \tilde{\bm{\tau}}_{-i})
$$

**Contest Function (Dyadic)**

$$
\chi_{ji} (\bm{m}) = \frac{ \rho_{ji} (\bm{W}; \bm{\alpha}) m_{ji} }{ \rho_{ji} (\bm{W}; \bm{\alpha}) m_{ji} + m_{ii} }
$$

**Reservation Values**

$$
\color{bcOrange} \underline{G}_{ji}(\bm{m}) \color{black} = \chi_{ji} (\bm{m})G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\bm{m}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

. . . 

- No war $\implies G_j(\tilde{\bm{\tau}}) \geq \color{bcOrange} \underline{G}_{ji}(\bm{m})$ for all $j, i$

. . . 

- Proposition `r Pc`: $\exists$ $\left\{ c_j^\star \right\}_{j \in \left\{1,..., N \right\}}$ such that no war occurs if $c_j > c_j^\star$ for all $j$.

## ($\Gamma^{\bm{\tau}}$) Trade Policy Announcements {id="policies"}

$$
\color{bcOrange} \underline{G}_{ji}(\bm{m}) \color{black} = \chi_{ji} (\bm{m}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\bm{m}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

. . . 

**Constrained Optimal Policies**

\begin{equation}
\begin{split}
\max_{ \tilde{\bm{\tau}}_i } & \quad G_i(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i})
\end{split}
\end{equation}

## ($\Gamma^{\bm{\tau}}$) Trade Policy Announcements

$$
\color{bcOrange} \underline{G}_{ji}(\bm{m}) \color{black} = \chi_{ji} (\bm{m}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\bm{m}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

**Constrained Optimal Policies**

\begin{equation}
\begin{split}
\max_{ \tilde{\bm{\tau}}_i } & \quad G_i(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \\
\text{subject to} & \quad G_j(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \geq \color{bcOrange} \underline{G}_{ji}(\bm{m}) \color{black} \text{ for all } j \neq i
\end{split}
\end{equation}

## ($\Gamma^{\bm{\tau}}$) Trade Policy Announcements

$$
\underline{G}_{ji}(\color{bcOrange} \bm{m} \color{black}) = \chi_{ji} (\color{bcOrange} \bm{m} \color{black}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\color{bcOrange}  \bm{m} \color{black}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

**Constrained Optimal Policies**

\begin{equation}
\begin{split}
\max_{ \tilde{\bm{\tau}}_i } & \quad G_i(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \\
\text{subject to} & \quad G_j(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \geq \underline{G}_{ji}( \color{bcOrange} \bm{m} \color{black}) \text{ for all } j \neq i
\end{split}
\end{equation}

## ($\Gamma^{\bm{\tau}}$) Trade Policy Announcements

$$
\underline{G}_{ji}(\color{bcOrange} \bm{m} \color{black}) = \chi_{ji} (\color{bcOrange} \bm{m} \color{black}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\color{bcOrange}  \bm{m} \color{black}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

**Constrained Optimal Policies**

\begin{equation}
\begin{split}
\tilde{\bm{\tau}}_i^\star( \color{bcOrange} \bm{m} \color{black}) = \argmax_{ \tilde{\bm{\tau}}_i } & \quad G_i(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \\
\text{subject to} & \quad G_j(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \geq \underline{G}_{ji}( \color{bcOrange} \bm{m} \color{black}) \text{ for all } j \neq i
\end{split}
\end{equation}

## ($\Gamma^{\bm{m}}$) Military Strategies

$$
\underline{G}_{ji}(\color{bcOrange} \bm{m} \color{black}) = \chi_{ji} (\color{bcOrange} \bm{m} \color{black}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\color{bcOrange}  \bm{m} \color{black}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

**Constrained Optimal Policies**

\begin{equation}
\begin{split}
\tilde{\bm{\tau}}_i^\star( \color{bcOrange} \bm{m} \color{black}) = \argmax_{ \tilde{\bm{\tau}}_i } & \quad G_i(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \\
\text{subject to} & \quad G_j(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \geq \underline{G}_{ji}( \color{bcOrange} \bm{m} \color{black}) \text{ for all } j \neq i
\end{split}
\end{equation}

**Optimal Military Strategies**

\begin{equation}
\begin{split}
\max_{ \color{bcOrange} \bm{m}_i \color{black} } & \quad G_i \left(\tilde{\bm{\tau}}^\star( \color{bcOrange} \bm{m}_i \color{black} ; \bm{m}_{-i}) \right)
\end{split}
\end{equation}

. . . 

$$
\color{bcOrange} \bm{m}_i = \begin{pmatrix} m_{i1} & \cdots & m_{iN} \end{pmatrix}
$$

- $\color{bcOrange} m_{ij}$: military effort $i$ dedicates toward threatening $j$ 

## ($\Gamma^{\bm{m}}$) Military Strategies {id="military"}

$$
\underline{G}_{ji}(\bm{m}) = \chi_{ji} (\bm{m}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\bm{m}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

**Constrained Optimal Policies**

\begin{equation}
\begin{split}
\tilde{\bm{\tau}}_i^\star(\bm{m}) = \argmax_{ \tilde{\bm{\tau}}_i } & \quad G_i(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \\
\text{subject to} & \quad G_j(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \geq \underline{G}_{ji}(\bm{m}) \text{ for all } j \neq i
\end{split}
\end{equation}

**Optimal Military Strategies**

\begin{equation}
\begin{split}
\max_{ \bm{m}_i } & \quad G_i \left(\tilde{\bm{\tau}}^\star( \bm{m}_i ; \bm{m}_{-i}) \right) \\
\text{subject to} & \quad \sum_j m_{ij} \leq \color{bcOrange} M_i
\end{split}
\end{equation}

## ($\Gamma^{\bm{m}}$) Military Strategies

$$
\underline{G}_{ji}(\bm{m}) = \chi_{ji} (\bm{m}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\bm{m}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

**Constrained Optimal Policies**

\begin{equation}
\begin{split}
\tilde{\bm{\tau}}_i^\star(\bm{m}) = \argmax_{ \tilde{\bm{\tau}}_i } & \quad G_i(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \\
\text{subject to} & \quad G_j(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \geq \underline{G}_{ji}(\bm{m}) \text{ for all } j \neq i
\end{split}
\end{equation}

**Optimal Military Strategies**

\begin{equation}
\begin{split}
\color{bcOrange} \bm{m}_i^\star \color{black} = \argmax_{ \bm{m}_i } & \quad G_i \left(\tilde{\bm{\tau}}^\star( \bm{m}_i ; \bm{m}_{-i}) \right) \\
\text{subject to} & \quad \sum_j m_{ij} \leq M_i
\end{split}
\end{equation}

## Estimation and Identification {.aligncenter}

$$
\left\{ \bm{\tau}, \bm{M} \right\} \rightarrow \bm{\theta}
$$

## Observables and Unobservables {id="observables"}

**Data**

- $\bm{\tau}$: policy barriers to trade (<a href="#/barriers">barriers</a>)
- $\bm{M}$: military expenditure

## Observables and Unobservables

**Data**

- $\bm{\tau}$: policy barriers to trade (<a href="#/barriers">barriers</a>)
- $\bm{M}$: military expenditure

```{r milex, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center", fig.height=5}

source("figs/milex.R")
milexFig

```

## Observables and Unobservables

**Data**

- $\bm{\tau}$: policy barriers to trade (<a href="#/barriers">barriers</a>)
- $\bm{M}$: military expenditure

**Structural Parameters**
$$
\bm{\theta} = \left\{ \bm{b}, \rho(\bm{W}) \right\}
$$

## Observables and Unobservables

**Data**

- $\bm{\tau}$: policy barriers to trade (<a href="#/barriers">barriers</a>)
- $\bm{M}$: military expenditure

**Structural Parameters**
$$
\bm{\theta} = \left\{ \color{bcOrange} \bm{b} \color{black}, \rho(\bm{W}) \right\}
$$

- $\color{bcOrange} \bm{b}$: governments' preferences

## Observables and Unobservables

**Data**

- $\bm{\tau}$: policy barriers to trade (<a href="#/barriers">barriers</a>)
- $\bm{M}$: military expenditure

**Structural Parameters**
$$
\bm{\theta} = \left\{ \bm{b}, \color{bcOrange} \rho(\bm{W}) \color{black} \right\}
$$

- $\bm{b}$: governments' preferences
- $\color{bcOrange} \rho(\bm{W})$: loss of strength gradient
  + $\bm{W}$: minimum geographic distance

## Observables and Unobservables

**Data**

- $\bm{\tau}$: policy barriers to trade (<a href="#/barriers">barriers</a>)
- $\bm{M}$: military expenditure

**Structural Parameters**
$$
\bm{\theta} = \left\{ \bm{b}, \rho(\bm{W}) \right\}
$$

- $\bm{b}$: governments' preferences
- $\rho(\bm{W})$: loss of strength gradient
  <!-- + $\bm{W}$: minimum geographic distance -->

**Measurement Error**
$$
\tau_{ij} = \tilde{\tau}_{ij}^\star(\bm{m}^\star; \bm{\theta}) - \epsilon_{ij} 
$$

. . . 

**Estimation Problem**

\begin{equation}
\begin{split}
\hat{\bm{\theta}} = \argmin_{\bm{\theta}} & \quad \sum_i \sum_j \left( \epsilon_{ij}(\bm{\theta}) \right)^2
\end{split}
\end{equation}

. . . 

- Reformulate as mathematical program with equilibrium constraints (MPEC) [@Su2012]

## Identification {id="identification"}

```{r tauhmI1, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

source("figs/tau.R")
tauhm(tau)

```

## Identification

```{r tauhmI2, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

source("figs/tau.R")
tauhm(tau, highlight="KOR")

```

## Thank You {.aligncenter}

[brendancooley.com](http://brendancooley.com)

[bcooley@princeton.edu](mailto:bcooley@princeton.edu)

## Table of Contents {id="toc"}

<div id="left">
1. <a href="#/introduction">Introduction</a>
2. <a href="#/approach">Approach</a>
3. <a href="#/cipe">Model</a>
4. <a href="#/economy">Economy</a>
5. <a href="#/wars">Wars</a>
6. <a href="#/policies">Policies</a>
7. <a href="#/military">Military Strategies</a>
8. <a href="#/observables">Estimation</a>
9. <a href="#/identification">Identification</a>
</div>

<div id="right">
1. <a href="#/economyA">Economy</a>
2. <a href="#/economyHats">Economy in Changes</a>
3. <a href="#/policyHats">Policy Problem in Changes</a>
3. <a href="#/multilateralcontest">Multilateral Contest Function</a>
4. <a href="#/sampleCountries">Sample Countries</a>
5. <a href="#/barriers">Policy Barriers</a>
6. <a href="#/freetrade">Free Trade</a>
7. <a href="#/mpec">MPEC</a>
</div>

## Economy (Consumption) {id="economyA"}

**Consumer's Problem**

\begin{equation*} \label{eq:consumer}
\begin{split}
\max & \quad U_i = Q_i^{\nu_i} S_i^{1 - \nu_i} \\
\text{subject to} & \quad P_i Q_i + P_i^s S_i \leq w_i L_i
\end{split}
\end{equation*}

**CES Preferences over Tradable Varieties**

$$
Q_i = \left( \int_{[0,1]} \alpha_{h(\omega)}^{\frac{1}{\sigma}} q_i(\omega)^{\frac{\sigma - 1}{\sigma}} d \omega \right)^{\frac{\sigma}{\sigma - 1}}
$$

**Tradable Price Index**

$$
P_i = \left( \int_{[0,1]} \alpha_{h(\omega)} p_i(\omega)^{1 - \sigma} d \omega \right)^{\frac{1}{1 - \sigma}}
$$

**Expenditure on Tradables**

$$
E_i^q = \nu_i I_i + D_i = P_i Q_i^\star
$$

<a href="#/moverview" style="float: right;">Back</a>

## Economy (Production)

**Costs**

\begin{equation} \label{eq:c}
c_i = w_i^{1 - \beta} P_i^{\beta}
\end{equation}

- $w_i$ - cost of labor
- $P_i$ - cost of composite intermediate good
  + equivalent to composite consumption good

$$
E_i^x = \beta X_i
$$

**Local Prices**

$$
p_{ii}(\omega) = \frac{c_i}{z_i(\omega)}
$$

**Technology (Frechet)**

$$
F_i(z) = \text{Pr} \left\{ z_i(\omega) \leq z \right\} = \exp \left\{ - T_i z^{-\theta} \right\}
$$

## Economy (Equilibrium)

**Total Expenditure on Tradables**

$$
X_i = \underbrace{E_i^q + E_i^x}_{E_i} - D_i
$$

**Trade Shares**

$$
\Omega_{ij}^\star = \left\{ \omega \in [0,1] \left. \right\vert p_{ij}(\omega) \leq \min_{k \neq j} \left\{ p_{ik} \right\} \right\}
$$

$$
\lambda_{ij}(\boldsymbol{w}) = \frac{1}{E_i} \int_{\Omega_{ij}^\star} p_{ij}(\omega) q_i \left( p_{ij} (\omega) \right) d \omega
$$

**Market Clearing**

$$
X_i = \sum_{j=1}^N \lambda_{ji}(\boldsymbol{w}) E_j
$$

## Economy (Equilibrium in Changes) {id="economyHats"}

$$
\hat{r}_i = \frac{1}{r_i} \left( E_i \hat{E}_i(\hat{\bm{w}}) - \sum_j X_{ij}^{\text{cif}} \hat{X}_{ij}^{\text{cif}}(\hat{\bm{w}}) \right)
$$
$$
\hat{w}_i = \frac{1}{\nu_i w_i L_i} \left( \sum_j \left( (1 - \beta) X_{ji}^{\text{cif}} \hat{X}_{ji}^{\text{cif}}(\hat{\bm{w}}) \right) + (1 - \nu_i) r_i \hat{r}_i(\hat{\bm{w}}) \right)
$$
$$
\hat{E}_i(\hat{\bm{w}}) = \frac{1}{E_i} \left( E_i^q \hat{E}_i^q(\hat{\bm{w}}) + E_i^x \hat{E}_i^x(\hat{\bm{w}}) \right)
$$
$$
\hat{x}_{ij}(\hat{\bm{w}}) = \left( \hat{\tau}_{ij} \hat{w}_j^{1 - \beta} \hat{P}_j(\hat{\bm{w}})^\beta \right)^{-\theta} \hat{P}_i(\hat{\bm{w}})^{\theta}
$$
$$
\hat{P}_i(\hat{\bm{w}}) = \left( \sum_j x_{ij} \left( \hat{\tau}_{ij} \hat{w}_j^{1 - \beta} \hat{P}_j(\hat{\bm{w}})^\beta \right)^{-\theta} \right)^{-\frac{1}{\theta}}
$$
$$
1 = \sum_i y_i \hat{w}_i
$$

## Policy Problem in Changes {id="policyHats"}

**Government Welfare**

$$
\hat{G}_i(\hat{\bm{\tau}}; b_i) = \hat{V}_i \left( \hat{h}(\hat{\bm{\tau}}) \right)^{1 - b_i} \hat{r}_i \left(\hat{h}(\hat{\bm{\tau}}) \right)^{b_i}
$$

**Optimal Post-Conquest Policies**

\begin{equation*}
\begin{split}
\max_{\hat{\bm{\tau}}_j} & \quad \hat{G}_i(\hat{\bm{\tau}}_j; \hat{\tilde{\bm{\tau}}}_{-j}) \\
\text{subject to} & \quad \hat{\tau}_{jj} = 1
\end{split}
\end{equation*}

**Constrained Policy Problem in Changes**

\begin{equation*}
\begin{split}
\max_{ \hat{\tilde{\bm{\tau}}}_i } & \quad \hat{G}_i(\hat{\tilde{\bm{\tau}}}_i; \hat{\tilde{\bm{\tau}}}_{-i}) \\
\text{subject to} & \quad \hat{G}_j(\hat{\tilde{\bm{\tau}}}) - \hat{G}_j(\hat{\bm{\tau}}_i^{j \star}) + \hat{c} \left( \chi_{ji}(1; \bm{0}_{-j, -i}, \bm{m}) \right)^{-1} \geq 0 \quad \text{for all } j \neq i
\end{split}
\end{equation*}

## Multilateral Contest Function {.centercontent id="multilateralcontest"}

$$
\chi_{ij}(\bm{a}, \bm{m}) = \frac{ a_{ij} \rho_{ij}(\bm{W}; \bm{\alpha}) m_{ij} }{ \sum_k a_{kj} \rho_{kj}(\bm{W}; \bm{\alpha}) m_{kj} }
$$

<a href="#/contest">Back</a>

## Sample Countries {id="sampleCountries"}

```{r ccodes, echo=FALSE, warning=FALSE, message=FALSE}

source("figs/ccodes.R")

kable(ccodesT) %>% kable_styling(bootstrap_options = c("striped"))

```

## Policy Barriers to Trade, `r Y` {id="barriers"}

```{r tauhmA, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

source("figs/tau.R")
tauhm(tau)

```

<a href="#/introduction">Back (Intro)</a> &nbsp; <a href="#/observables">Back (Estimation)</a>

## Welfare Under Free Trade {id="freetrade"}

```{r Ghatft, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

source("figs/Ghatft.R")
GhatftFig + theme(aspect.ratio=1)

```

<a href="#/economyLast" style="float: right;">Back</a>

## Mathematical Program with Equilibrium Constraints {id="mpec"}

**Equilibrium Constraints**

\begin{align*}
\nabla_{\hat{\bm{x}}_i} \mathcal{L}_i^{\hat{\bm{x}}}(\hat{\bm{x}}_i; \bm{m}, \bm{\lambda}_i^{\bm{\chi}}, \bm{\lambda}_i^{\hat{\bm{w}}}, \bm{\theta}_m) &= \bm{0} \quad \text{for all } i \\
\lambda_{ij}^{\bm{\chi}} \left( \hat{G}_j(\hat{\bm{w}}; \bm{\theta}_m) - \hat{G}_j \left( \hat{\bm{\tau}}_i^{j \star}(\bm{\theta}_m) \right) + \hat{c} \left( \chi_{ji}(\bm{m}, \bm{\theta}_m) \right)^{-1} \right) &= 0 \quad \text{for all } i, j \\
\hat{\bm{w}} - \hat{h}(\hat{\tilde{\bm{\tau}}}) &= \bm{0} \\
\nabla_{\bm{m}} \mathcal{L}_i^{\bm{m}}(\bm{m}; \bm{\lambda}^{\bm{m}}, \bm{\theta}_m) &= \bm{0} \quad \text{for all } i \\
\lambda_i^{\bm{m}} \left( M_i - \sum_k m_{jk} \right) &= 0 \quad \text{for all } i
\end{align*}

**Estimation Problem**

\begin{equation*}
\begin{split}
\min_{\bm{\theta}_m, \bm{m}, \bm{\lambda}^{\bm{\chi}}, \bm{\lambda}^{\bm{w}}, \bm{\lambda}^{\bm{m}}} & \quad \sum_i \sum_j \epsilon_{ij}(\bm{\theta}_m)^2 \\
\text{subject to} & \quad g(\bm{1}, \bm{\theta}_m, \bm{m}, \bm{\lambda}^{\bm{\chi}}, \bm{\lambda}^{\bm{w}}, \bm{\lambda}^{\bm{m}}) = \bm{0}
\end{split}
\end{equation*}

<!-- hide references -->
<hr style="height:30em; visibility:hidden;" />