---
title: "Trade Policy in the Shadow of Power"
subtitle: "Quantifying Military Coercion in the International System"
date: "9 April 2020"
author: Brendan Cooley
position: Ph.D. Candidate
institution: Princeton University
email: "bcooley (at) princeton.edu"
note: These slides available at brendancooley.com/tpsp

bibliography: bib/library.bib
biblio-style: apsr

backgroundTitle: "02_figs/img/cover.jpg"

output:
  revealjs::revealjs_presentation:
    template: "css/cooley-reveal.html"
    css: "css/cooley-reveal.css"
    backgroundTransition: none
    transition: none
    self_contained: false
    # reveal_plugins: ["notes"]
    lib_dir: index_files
    fig_caption: true
    reveal_options:
      slideNumber: false
      progress: false
      controls: true
---


```{r references, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

helperPath <- "~/Dropbox (Princeton)/14_Software/R/"
helperFiles <- list.files(helperPath)
for (i in helperFiles) {
  source(paste0(helperPath, i))
}

libs <- c("tidyverse", "reticulate", "patchwork")
ipak(libs)

Sys.setenv(KMP_DUPLICATE_LIB_OK="True")

size <- "mid/"
sections_dir <- "03_sections/"
code_dir <- "01_code/"
figs_dir <- "02_figs/"
slides_dir <- "04_slides/"

# setup bib
mkdir("bib/")
file.copy("~/Dropbox (Princeton)/References/library.bib", "bib/library.bib")

# references from paper
if (file.exists('references.RData')) load('references.RData')

```

# Introduction {.aligncenter id="introduction"} 

```{r, child=paste0(slides_dir, "01_intro.rmd")}
```

# Data {.aligncenter id="data"}

```{r, child=paste0(slides_dir, "02_data.rmd")}
```

# Model {.aligncenter id="model"}

```{r, child=paste0(slides_dir, "03_model.rmd")}
```

# Estimation {.aligncenter id="estimation"}

```{r, child=paste0(slides_dir, "04_estimation.rmd")}
```

# Results {.aligncenter id="results"}

```{r, child=paste0(slides_dir, "05_results.rmd")}
```

# Counterfactuals {.aligncenter id="cfct"}

```{r, child=paste0(slides_dir, "06_cfct.rmd")}
```

# Conclusions {.aligncenter id="conclusions"}

```{r, child=paste0(slides_dir, "07_conclusion.rmd")}
```

# Thank You {.aligncenter}

## Thank You {.aligncenter}

[brendancooley.com](http://brendancooley.com)

[bcooley@princeton.edu](mailto:bcooley@princeton.edu)

# Appendix: Introduction {.aligncenter id="intro_apdx"}

```{r, child=paste0(slides_dir, "01_intro_apdx.rmd")}
```

# Appendix: Data {.aligncenter id="data_apdx"}

```{r, child=paste0(slides_dir, "02_data_apdx.rmd")}
```

# Appendix: Model {.aligncenter id="model_apdx"}

```{r, child=paste0(slides_dir, "03_model_apdx.rmd")}
```

# Appendix: Estimation {.aligncenter id="estimation_apdx"}

```{r, child=paste0(slides_dir, "04_estimation_apdx.rmd")}
```

# Appendix: Results {.aligncenter id="results_apdx"}

```{r, child=paste0(slides_dir, "05_results_apdx.rmd")}
```

# Appendix: Counterfactuals {.aligncenter id="results_apdx"}

```{r, child=paste0(slides_dir, "06_cfct_apdx.rmd")}
```

<!-- hide references -->
<hr style="height:30em; visibility:hidden;" />
 