---
title: "Trade Policy in the Shadow of Power"
subtitle: "Quantifying Military Coercion in the International System"
date: "1 September 2019"
author: Brendan Cooley
position: Ph.D. Candidate
institution: Princeton University
email: "bcooley (at) princeton.edu"

bibliography: /Users/bcooley/Dropbox (Princeton)/References/library.bib
biblio-style: apsr

backgroundTitle: "figs/cover.jpg"

output:
  revealjs::revealjs_presentation:
    template: "css/cooley-reveal.html"
    css: "css/cooley-reveal.css"
    backgroundTransition: none
    transition: none
    self_contained: false
    # reveal_plugins: ["notes"]
    lib_dir: index_files
    reveal_options:
      slideNumber: false
      progress: false
      controls: false      
    includes:
      after_body: "css/plugins.html"
---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

helperPath <- "~/Dropbox (Princeton)/14_Software/R/"
helperFiles <- list.files(helperPath)
for (i in helperFiles) {
  source(paste0(helperPath, i))
}

libs <- c("tidyverse", "patchwork")
ipak(libs)

analysisPath <- "working/analysis/"
dataPath <- paste0(analysisPath, "tpsp_data/")
resultsPath <- paste0(analysisPath, "results/")

# data
ccodes <- read_csv(paste0(dataPath, "ccodes.csv"), col_names=FALSE)
Y <- read_csv(paste0(dataPath, "year.csv"), col_names=FALSE) %>% pull(.)
tau <- read_csv(paste0(dataPath, "tau.csv"), col_names=FALSE)

# results
Ghatft <- read_csv(paste0(resultsPath, "Ghatft.csv"), col_names=FALSE)
rcv0 <- read_csv(paste0(resultsPath, "rcv0.csv"), col_names=FALSE)
rcv1 <- read_csv(paste0(resultsPath, "rcv1.csv"), col_names=FALSE)

# references from paper
if (file.exists('references.RData')) load('references.RData')

```

## Power and Preferences {id="introduction"}

**Anarchy and Inference**

- Anarchy $\implies$ powerful governments can impose policies on others by force
- Bargaining critique: policy adjustment should occur through diplomacy
  + @Brito1985, @Fearon1995, @Art1996
- **Question:** Do observed policies reflect **preferences** of the governments that adopted them or **constraints of anarchy?**

. . . 

**Trade Policy: What Do Governments Want?**

- Mercantilist preferences: openness abroad and some closure at home
  + @Grossman1994, @Gawande2009
- Coercion: powerful governments impose openness abroad
  + Gunboat diplomacy [@Findlay2007]

. . . 

**Trade Policy: Does It Matter?**

- Tariffs small, aggregate policy-induced trade frictions large
  + @Cooley2019b (<a href="#/barriers">barriers</a>)
- Welfare effects of trade frictions
  + @Autor2013, @Costinot2015, @Goldberg2016

## Anarchy and Inference: Approach

**Ideal Experiment**

- Dispatch U.S. military (for example) on long-term mission to Pluto
- Attribute changes in trade policy to latent effect of military coercion

. . . 

**A Coercive International Political Economy**

$$
\left\{ \bm{\theta}, \bm{M} \right\} \rightarrow \bm{\tau}
$$

- $\bm{\theta}$ -- structural parameters (power and preferences)
- $\bm{M}$ -- governments' military endowment (expenditure)
- $\bm{\tau}$ -- governments' trade policies

. . . 

**Estimation:** $\left\{ \bm{\tau}, \bm{M} \right\} \rightarrow \bm{\theta}$

. . . 

**Counterfactuals:** $\left\{ \bm{\theta}^\prime, \bm{M}^\prime \right\} \rightarrow \bm{\tau}^\prime$

- Shadow of power
  + Effect of changing military endowments on trade policy
- Liberal/commercial peace
  + Effect of changing preferences for openness on military strategies

## Model {.aligncenter}

$$
\left\{ \bm{\theta}, \bm{M} \right\} \rightarrow \bm{\tau}
$$

## Coercive International Political Economy

- Governments indexed $i \in \left\{ 1, ..., N \right\}$

. . . 

**Sequence**

1. ($\Gamma^{\bm{m}}$) Governments set military strategies
    + allocations of effort over potential wars
2. ($\Gamma^{\bm{\tau}}$) Governments make trade policy announcements
3. ($\Gamma^{\bm{a}}$) Wars
    + Winners choose trade policies for vanquished governments
4. ($h(\bm{\tau})$) Economic (general equilibrium) consequences of trade policies

. . . 

**Payoffs**

$$
G_i \left( h(\bm{\tau}), \bm{a} \right)
$$

## ($h(\bm{\tau})$) Economy

$$
\bm{\tau} = \begin{pmatrix}
\tau_{11} & \cdots & \cdots & \cdots & \tau_{1N} \\
\vdots & \ddots & \vdots & \iddots & \vdots \\
\vdots & \cdots & \tau_{ij} & \cdots & \vdots \\
\vdots & \iddots & \vdots & \ddots & \vdots \\
\tau_{N1} & \cdots & \cdots & \cdots & \tau_{NN}
\end{pmatrix}
$$

## ($h(\bm{\tau})$) Economy

$$
\bm{\tau} = \begin{pmatrix}
\tau_{11} & \cdots & \cdots & \cdots & \tau_{1N} \\
\vdots & \ddots & \vdots & \iddots & \vdots \\
\vdots & \cdots & \color{bcOrange} \tau_{ij} & \cdots & \vdots \\
\vdots & \iddots & \vdots & \ddots & \vdots \\
\tau_{N1} & \cdots & \cdots & \cdots & \tau_{NN}
\end{pmatrix}
$$

<hr style="height:2em; visibility:hidden;" />

- $\color{bcOrange} \tau_{ij}$: trade barrier government $i$ imposes on imports from $j$
- $\color{bcOrange} \tau_{ij} \color{black} - 1$: ad-valorem tariff equivalent
- $\tau_{ij} = 1 \implies$ free trade
- $\tau_{ii} = 1$ for all $i$

## ($h(\bm{\tau})$) Economy

$$
\bm{\tau} = \begin{pmatrix}
\color{bcOrange} \tau_{11} & \color{bcOrange} \cdots & \color{bcOrange} \cdots & \color{bcOrange} \cdots & \color{bcOrange} \tau_{1N} \\
\vdots & \ddots & \vdots & \iddots & \vdots \\
\vdots & \cdots & \tau_{ij} & \cdots & \vdots \\
\vdots & \iddots & \vdots & \ddots & \vdots \\
\tau_{N1} & \cdots & \cdots & \cdots & \tau_{NN}
\end{pmatrix}
$$

<hr style="height:2em; visibility:hidden;" />

$$
\color{bcOrange} \bm{\tau}_1 = \begin{pmatrix} \tau_{11} & \cdots & \cdots & \cdots & \tau_{1N}
\end{pmatrix}
$$

<hr style="height:2em; visibility:hidden;" />

- Government 1's trade policy

## ($h(\bm{\tau})$) Economy

$$
\color{bcOrange} \bm{\tau} \color{black} = \begin{pmatrix}
\tau_{11} & \cdots & \cdots & \cdots & \tau_{1N} \\
\vdots & \ddots & \vdots & \iddots & \vdots \\
\vdots & \cdots & \tau_{ij} & \cdots & \vdots \\
\vdots & \iddots & \vdots & \ddots & \vdots \\
\tau_{N1} & \cdots & \cdots & \cdots & \tau_{NN}
\end{pmatrix}
$$

<hr style="height:2em; visibility:hidden;" />

$$
\color{bcOrange} h(\bm{\tau}) \rightarrow \begin{pmatrix}
w_1 \\
\vdots \\
w_N
\end{pmatrix} = \bm{w}
$$

## ($h(\bm{\tau})$) Economy

$$
h(\bm{\tau}) \rightarrow \begin{pmatrix}
w_1 \\
\vdots \\
w_N
\end{pmatrix} = \color{bcOrange} \bm{w}
$$

. . . 

<hr style="height:1em; visibility:hidden;" />

- $V_i( \color{bcOrange} \bm{w} \color{black})$: welfare of representative consumer in $i$
- $X_{ij}(\color{bcOrange} \bm{w} \color{black})$: $i$'s imports of goods from $j$
- Rents (tariff revenue):

$$
r_i(\color{bcOrange} \bm{w} \color{black}) = \sum_j (\tau_{ij} - 1) X_{ij}(\color{bcOrange} \bm{w} \color{black})
$$

. . . 

**Government Objective**

$$
G_i = V_i( \color{bcOrange} \bm{w} \color{black})^{1 - b_i} r_i(\color{bcOrange} \bm{w} \color{black})^{b_i}
$$

## ($h(\bm{\tau})$) Economy {id="economyLast"}

$$
h(\bm{\tau}) \rightarrow \begin{pmatrix}
w_1 \\
\vdots \\
w_N
\end{pmatrix} = \bm{w}
$$

<hr style="height:1em; visibility:hidden;" />

- $V_i(\bm{w})$: welfare of representative consumer in $i$
- $X_{ij}(\bm{w})$: $i$'s imports of goods from $j$
- Rents (tariff revenue):

$$
r_i(\bm{w} \color{black}) = \sum_j (\tau_{ij} - 1) X_{ij}(\bm{w})
$$

**Government Objective**

$$
G_i = V_i(\bm{w})^{ \color{bcOrange} 1 - b_i \color{black} } r_i(\bm{w})^{\color{bcOrange} b_i \color{black} }
$$

. . . 

- $\color{bcOrange} b_i = 0$: government maximizes consumer welfare
- $\color{bcOrange} b_i = 1$: government maximizes rents
- <a href="#/freetrade">Free Trade Counterfactual</a>

## ($\Gamma^{\bm{a}}$) Wars

**Optimal Post-Conquest Policies**

$$
\bm{\tau}_j^{i \star} = \argmax_{\bm{\tau}_j} \quad G_i(\bm{\tau}_j ; \tilde{\bm{\tau}}_{-j})
$$

## ($\Gamma^{\bm{a}}$) Wars

**Optimal Post-Conquest Policies**

$$
\color{bcOrange} \bm{\tau}_j^{i \star} \color{black} = \argmax_{\bm{\tau}_j} \quad G_{\color{bcOrange} i} \color{black} (\bm{\tau}_{\color{bcOrange} j} \color{black} ; \tilde{\bm{\tau}}_{-j})
$$

- $\color{bcOrange} \bm{\tau}_j^{i \star}$: trade policies in $\color{bcOrange} j$ imposed by government $\color{bcOrange} i$ post-conquest

## ($\Gamma^{\bm{a}}$) Wars {id="wars_rcv"}

**Optimal Post-Conquest Policies**

$$
\color{bcOrange} \bm{\tau}_j^{i \star} \color{black} = \argmax_{\bm{\tau}_j} \quad G_{i}(\bm{\tau}_{j}; \tilde{\bm{\tau}}_{-j})
$$

- $\color{bcOrange} \bm{\tau}_j^{i \star}$: trade policies in $j$ imposed by government $i$ post-conquest

**Conquest Values**

$$
G_i(\color{bcOrange} \bm{\tau}_j^{i \star} \color{black} ; \tilde{\bm{\tau}}_{-j})
$$

- <a href="#/rcv">Conquest Values (Empirical)</a>

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_i(\bm{\tau}_j^{i \star} \color{black} ; \tilde{\bm{\tau}}_{-j})
$$

. . . 

**Contest Function (Dyadic)**

$$
\chi_{ji}(\bm{m}) = \frac{ \rho_{ji}(\bm{W}; \bm{\alpha}) m_{ji} }{ \rho_{ji}(\bm{W}; \bm{\alpha}) m_{ji} + m_{ii} }
$$

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_i(\bm{\tau}_j^{i \star} \color{black} ; \tilde{\bm{\tau}}_{-j})
$$

**Contest Function (Dyadic)**

$$
\color{bcOrange} \chi_{ji} \color{black} (\bm{m}) = \frac{ \rho_{ji}(\bm{W}; \bm{\alpha}) m_{ji} }{ \rho_{ji}(\bm{W}; \bm{\alpha}) m_{ji} + m_{ii} }
$$

- $\color{bcOrange} \chi_{ji}$: probability $\color{bcOrange} j$ successfully conquers $\color{bcOrange} i$

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_i(\bm{\tau}_j^{i \star} \color{black} ; \tilde{\bm{\tau}}_{-j})
$$

**Contest Function (Dyadic)**

$$
\chi_{ji}( \color{bcOrange} \bm{m} \color{black}) = \frac{ \rho_{ji}(\bm{W}; \bm{\alpha}) \color{bcOrange} m_{ji} \color{black} }{ \rho_{ji}(\bm{W}; \bm{\alpha}) \color{bcOrange} m_{ji} \color{black} + \color{bcOrange} m_{ii} \color{black} }
$$

- $\chi_{ji}$: probability $j$ successfully conquers $i$
- $\color{bcOrange} \bm{m}$: military effort
- $\color{bcOrange} m_{ji}$: effort $j$ dedicates toward threatening $i$
- $\color{bcOrange} m_{ii}$: effort $i$ dedicates toward self-defense

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_i(\bm{\tau}_j^{i \star} \color{black} ; \tilde{\bm{\tau}}_{-j})
$$

**Contest Function (Dyadic)**

$$
\chi_{ji}(\bm{m}) = \frac{ \color{bcOrange} \rho_{ji} \color{black} (\bm{W}; \bm{\alpha}) m_{ji} }{ \color{bcOrange} \rho_{ji} \color{black} (\bm{W}; \bm{\alpha}) m_{ji} + m_{ii} }
$$

- $\chi_{ji}$: probability $j$ successfully conquers $i$
- $\bm{m}$: military effort
- $m_{ji}$: effort $j$ dedicates toward threatening $i$
- $m_{ii}$: effort $i$ dedicates toward self-defense
- $\color{bcOrange} \rho_{ji} \color{black} \in [0, 1]$: loss of strength gradient

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_i(\bm{\tau}_j^{i \star} \color{black} ; \tilde{\bm{\tau}}_{-j})
$$

**Contest Function (Dyadic)**

$$
\chi_{ji}(\bm{m}) = \frac{ \rho_{ji} (\color{bcOrange} \bm{W} \color{black} ; \bm{\alpha}) m_{ji} }{ \rho_{ji} ( \color{bcOrange} \bm{W} \color{black} ; \bm{\alpha}) m_{ji} + m_{ii} }
$$

- $\chi_{ji}$: probability $j$ successfully conquers $i$
- $\bm{m}$: military effort
- $m_{ji}$: effort $j$ dedicates toward threatening $i$
- $m_{ii}$: effort $i$ dedicates toward self-defense
- $\rho_{ji} \in [0, 1]$: loss of strength gradient
- $\color{bcOrange} \bm{W}$: dyadic geography

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_i(\bm{\tau}_j^{i \star} \color{black} ; \tilde{\bm{\tau}}_{-j})
$$

**Contest Function (Dyadic)**

$$
\color{bcOrange} \chi_{ji} (\bm{m}) \color{black} = \frac{ \rho_{ji} (\bm{W}; \bm{\alpha}) m_{ji} }{ \rho_{ji} (\bm{W}; \bm{\alpha}) m_{ji} + m_{ii} }
$$

**Reservation Values**

$$
\color{bcOrange} \chi_{ji} (\bm{m}) \color{black} G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \color{bcOrange}  \left( 1 - \chi_{ji} (\bm{m}) \right) \color{black} G_j(\tilde{\bm{\tau}}) - c_j
$$

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_j(\bm{\tau}_i^{j \star} \color{black} ; \tilde{\bm{\tau}}_{-i})
$$

**Contest Function (Dyadic)**

$$
\chi_{ji} (\bm{m}) = \frac{ \rho_{ji} (\bm{W}; \bm{\alpha}) m_{ji} }{ \rho_{ji} (\bm{W}; \bm{\alpha}) m_{ji} + m_{ii} }
$$

**Reservation Values**

$$
\chi_{ji} (\bm{m}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ij} (\bm{m}) \right) G_j(\tilde{\bm{\tau}}) - \color{bcOrange} c_j
$$

- $\color{bcOrange} c_j$: war cost

## ($\Gamma^{\bm{a}}$) Wars

**Conquest Values**

$$
G_j(\bm{\tau}_i^{j \star} \color{black} ; \tilde{\bm{\tau}}_{-i})
$$

**Contest Function (Dyadic)**

$$
\chi_{ji} (\bm{m}) = \frac{ \rho_{ji} (\bm{W}; \bm{\alpha}) m_{ji} }{ \rho_{ji} (\bm{W}; \bm{\alpha}) m_{ji} + m_{ii} }
$$

**Reservation Values**

$$
\color{bcOrange} \underline{G}_{ji}(\bm{m}) \color{black} = \chi_{ji} (\bm{m})G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\bm{m}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

. . . 

- No war $\implies G_j(\tilde{\bm{\tau}}) \geq \color{bcOrange} \underline{G}_{ji}(\bm{m})$ for all $j, i$

. . . 

- Proposition `r Pc`: $\exists$ $\left\{ c_j^\star \right\}_{j \in \left\{1,..., N \right\}}$ such that no war occurs if $c_j > c_j^\star$ for all $j$.

## ($\Gamma^{\bm{\tau}}$) Trade Policy Announcements

$$
\color{bcOrange} \underline{G}_{ji}(\bm{m}) \color{black} = \chi_{ji} (\bm{m}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\bm{m}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

. . . 

**Constrained Optimal Policies**

\begin{equation}
\begin{split}
\max_{ \tilde{\bm{\tau}}_i } & \quad G_i(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i})
\end{split}
\end{equation}

## ($\Gamma^{\bm{\tau}}$) Trade Policy Announcements

$$
\color{bcOrange} \underline{G}_{ji}(\bm{m}) \color{black} = \chi_{ji} (\bm{m}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\bm{m}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

**Constrained Optimal Policies**

\begin{equation}
\begin{split}
\max_{ \tilde{\bm{\tau}}_i } & \quad G_i(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \\
\text{subject to} & \quad G_j(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \geq \color{bcOrange} \underline{G}_{ji}(\bm{m}) \color{black} \text{ for all } j \neq i
\end{split}
\end{equation}

## ($\Gamma^{\bm{\tau}}$) Trade Policy Announcements

$$
\underline{G}_{ji}(\color{bcOrange} \bm{m} \color{black}) = \chi_{ji} (\color{bcOrange} \bm{m} \color{black}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\color{bcOrange}  \bm{m} \color{black}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

**Constrained Optimal Policies**

\begin{equation}
\begin{split}
\max_{ \tilde{\bm{\tau}}_i } & \quad G_i(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \\
\text{subject to} & \quad G_j(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \geq \underline{G}_{ji}( \color{bcOrange} \bm{m} \color{black}) \text{ for all } j \neq i
\end{split}
\end{equation}

## ($\Gamma^{\bm{\tau}}$) Trade Policy Announcements

$$
\underline{G}_{ji}(\color{bcOrange} \bm{m} \color{black}) = \chi_{ji} (\color{bcOrange} \bm{m} \color{black}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\color{bcOrange}  \bm{m} \color{black}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

**Constrained Optimal Policies**

\begin{equation}
\begin{split}
\tilde{\bm{\tau}}_i^\star( \color{bcOrange} \bm{m} \color{black}) = \argmax_{ \tilde{\bm{\tau}}_i } & \quad G_i(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \\
\text{subject to} & \quad G_j(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \geq \underline{G}_{ji}( \color{bcOrange} \bm{m} \color{black}) \text{ for all } j \neq i
\end{split}
\end{equation}

## ($\Gamma^{\bm{m}}$) Military Strategies

$$
\underline{G}_{ji}(\color{bcOrange} \bm{m} \color{black}) = \chi_{ji} (\color{bcOrange} \bm{m} \color{black}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\color{bcOrange}  \bm{m} \color{black}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

**Constrained Optimal Policies**

\begin{equation}
\begin{split}
\tilde{\bm{\tau}}_i^\star( \color{bcOrange} \bm{m} \color{black}) = \argmax_{ \tilde{\bm{\tau}}_i } & \quad G_i(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \\
\text{subject to} & \quad G_j(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \geq \underline{G}_{ji}( \color{bcOrange} \bm{m} \color{black}) \text{ for all } j \neq i
\end{split}
\end{equation}

**Optimal Military Strategies**

\begin{equation}
\begin{split}
\max_{ \color{bcOrange} \bm{m}_i \color{black} } & \quad G_i \left(\tilde{\bm{\tau}}^\star( \color{bcOrange} \bm{m}_i \color{black} ; \bm{m}_{-i}) \right)
\end{split}
\end{equation}

. . . 

$$
\color{bcOrange} \bm{m}_i = \begin{pmatrix} m_{i1} & \cdots & m_{iN} \end{pmatrix}
$$

- $\color{bcOrange} m_{ij}$: military effort $i$ dedicates toward threatening $j$ 

## ($\Gamma^{\bm{m}}$) Military Strategies

$$
\underline{G}_{ji}(\bm{m}) = \chi_{ji} (\bm{m}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\bm{m}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

**Constrained Optimal Policies**

\begin{equation}
\begin{split}
\tilde{\bm{\tau}}_i^\star(\bm{m}) = \argmax_{ \tilde{\bm{\tau}}_i } & \quad G_i(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \\
\text{subject to} & \quad G_j(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \geq \underline{G}_{ji}(\bm{m}) \text{ for all } j \neq i
\end{split}
\end{equation}

**Optimal Military Strategies**

\begin{equation}
\begin{split}
\max_{ \bm{m}_i } & \quad G_i \left(\tilde{\bm{\tau}}^\star( \bm{m}_i ; \bm{m}_{-i}) \right) \\
\text{subject to} & \quad \sum_j m_{ij} \leq \color{bcOrange} M_i
\end{split}
\end{equation}

## ($\Gamma^{\bm{m}}$) Military Strategies

$$
\underline{G}_{ji}(\bm{m}) = \chi_{ji} (\bm{m}) G_j(\bm{\tau}_i^{j \star}; \tilde{\bm{\tau}}_{-j}) + \left( 1 - \chi_{ji} (\bm{m}) \right) G_j(\tilde{\bm{\tau}}) - c_j
$$

**Constrained Optimal Policies**

\begin{equation}
\begin{split}
\tilde{\bm{\tau}}_i^\star(\bm{m}) = \argmax_{ \tilde{\bm{\tau}}_i } & \quad G_i(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \\
\text{subject to} & \quad G_j(\tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i}) \geq \underline{G}_{ji}(\bm{m}) \text{ for all } j \neq i
\end{split}
\end{equation}

**Optimal Military Strategies**

\begin{equation}
\begin{split}
\color{bcOrange} \bm{m}_i^\star \color{black} = \argmax_{ \bm{m}_i } & \quad G_i \left(\tilde{\bm{\tau}}^\star( \bm{m}_i ; \bm{m}_{-i}) \right) \\
\text{subject to} & \quad \sum_j m_{ij} \leq M_i
\end{split}
\end{equation}

## Estimation {.aligncenter}

$$
\left\{ \bm{\tau}, \bm{M} \right\} \rightarrow \bm{\theta}
$$

## Observables and Unobservables {id="observables"}

**Data**

- $\bm{\tau}$: policy barriers to trade (<a href="#/barriers">barriers</a>)
- $\bm{M}$: military expenditure (<a href="#/milex">milex</a>)

. . . 

**Structural Parameters**
$$
\bm{\theta} = \left\{ \bm{b}, \rho(\bm{W}) \right\}
$$

## Observables and Unobservables

**Data**

- $\bm{\tau}$: policy barriers to trade (<a href="#/barriers">barriers</a>)
- $\bm{M}$: military expenditure (<a href="#/milex">milex</a>)

**Structural Parameters**
$$
\bm{\theta} = \left\{ \color{bcOrange} \bm{b} \color{black}, \rho(\bm{W}) \right\}
$$

- $\color{bcOrange} \bm{b}$: governments' preferences

## Observables and Unobservables

**Data**

- $\bm{\tau}$: policy barriers to trade (<a href="#/barriers">barriers</a>)
- $\bm{M}$: military expenditure (<a href="#/milex">milex</a>)

**Structural Parameters**
$$
\bm{\theta} = \left\{ \bm{b}, \color{bcOrange} \rho(\bm{W}) \color{black} \right\}
$$

- $\bm{b}$: governments' preferences
- $\color{bcOrange} \rho(\bm{W})$: loss of strength gradient
  + $\bm{W}$: minimum geographic distance

## Observables and Unobservables

**Data**

- $\bm{\tau}$: policy barriers to trade (<a href="#/barriers">barriers</a>)
- $\bm{M}$: military expenditure (<a href="#/milex">milex</a>)

**Structural Parameters**
$$
\bm{\theta} = \left\{ \bm{b}, \rho(\bm{W}) \right\}
$$

- $\bm{b}$: governments' preferences
- $\rho(\bm{W})$: loss of strength gradient
  + $\bm{W}$: minimum geographic distance

**Structural Residual**
$$
\epsilon_{ij}(\bm{\theta}) = \tilde{\tau}_{ij}^\star(\bm{m}^\star; \bm{\theta}) - \tau_{ij}
$$

. . . 

**Estimation Problem**

\begin{equation}
\begin{split}
\hat{\bm{\theta}} = \argmin_{\bm{\theta}} & \quad \sum_i \sum_j \left( \epsilon_{ij}(\bm{\theta}) \right)^2
\end{split}
\end{equation}

. . . 

- Reformulate as mathematical program with equilibrium constraints (MPEC) [@Su2012]

## Conclusion

**Counterfactuals**
$$
\left\{ \left\{ \bm{b}^\prime, \rho(\bm{W}) \right\}, \bm{M}^\prime \right\} \rightarrow \left\{ \bm{\tau}^\prime, \bm{m}^\prime \right\}
$$

## Conclusion

**Counterfactuals**
$$
\left\{ \left\{ \bm{b}, \rho(\bm{W}) \right\}, \color{bcOrange} \bm{M}^\prime \color{black} \right\} \rightarrow \left\{ \color{bcOrange} \bm{\tau}^\prime \color{black}, \bm{m}^\prime \right\}
$$

- Shadow of power ($\color{bcOrange} \bm{M}^\prime \rightarrow \bm{\tau}^\prime$)

## Conclusion

**Counterfactuals**
$$
\left\{ \left\{ \color{bcOrange} \bm{b}^\prime \color{black}, \rho(\bm{W}) \right\}, \bm{M} \right\} \rightarrow \left\{ \color{bcOrange} \bm{\tau}^\prime, \bm{m}^\prime \color{black} \right\}
$$

- Shadow of power ($\bm{M}^\prime \rightarrow \bm{\tau}^\prime$)
- Liberal peace ($\color{bcOrange} \bm{b}^\prime \color{black} \rightarrow \color{bcOrange} \bm{\tau}^\prime, \bm{m}^\prime \color{black}$)

. . . 

**Results**

- Coming soon...

## Thank You {.aligncenter}

[brendancooley.com](http://brendancooley.com)

[bcooley@princeton.edu](mailto:bcooley@princeton.edu)

## Policy Barriers to Trade, `r Y` {id="barriers"}

```{r tauhm, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

source("figs/tau.R")
tauhm(tau)

```

<a href="#/introduction">Back (Intro)</a> &nbsp; <a href="#/observables">Back (Estimation)</a>

## Welfare Under Free Trade {id="freetrade"}

```{r Ghatft, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

source("figs/Ghatft.R")
GhatftFig + theme(aspect.ratio=1)

```

<a href="#/economyLast" style="float: right;">Back</a>

## Conquest Values (Empirical) {id="rcv"}

```{r rcv, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

source("figs/rcv.R")
rcvhm(rcv0, 0, mint, maxt) + rcvhm(rcv1, 1, mint, maxt)

```

<a href="#/wars_rcv" style="float: right;">Back</a>

## Military Expenditure {id="milex"}

```{r milex, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

source("figs/milex.R")
milexFig

```

<a href="#/observables" style="float: right;">Back</a>

<!-- hide references -->
<hr style="height:30em; visibility:hidden;" />