---
title: "Trade Policy in the Shadow of Power"
subtitle: "Quantifying Military Coercion in the International System"
date: "9 April 2020"
author: Brendan Cooley
position: Ph.D. Candidate
institution: Princeton University
email: "bcooley (at) princeton.edu"
note: These slides available at brendancooley.com/tpsp

bibliography: /Users/brendancooley/Dropbox (Princeton)/References/library.bib
biblio-style: apsr

backgroundTitle: "02_figs/cover.jpg"

output:
  revealjs::revealjs_presentation:
    template: "css/cooley-reveal.html"
    css: "css/cooley-reveal.css"
    backgroundTransition: none
    transition: none
    self_contained: false
    # reveal_plugins: ["notes"]
    lib_dir: index_files
    reveal_options:
      slideNumber: false
      progress: false
      controls: false      
    includes:
      after_body: "css/plugins.html"
---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

code_dir <- "01_code/"
figs_dir <- "02_figs/"
slides_dir <- "slides/"

size = "mid/"

# references from paper
if (file.exists('references.RData')) load('references.RData')

```

```{r, child="slides/introduction.rmd"}
```

# Table of Contents {id="toc"}

<div id="left">
1. <a href="#/introduction">Introduction</a>
2. <a href="#/approach">Approach</a>
3. <a href="#/cipe">Model</a>
4. <a href="#/br">Equilibrium</a>
5. <a href="#/estimation">Estimation</a>
6. <a href="#/results">Results</a>
</div>

<div id="right">
1. <a href="#/economy">Economy (Overview)</a>
2. <a href="#/barriers">Estimated Dyadic Policy Barriers</a>
3. <a href="#/Gobj">Government Objective</a>
4. <a href="#/economyA">Economy (GE)</a>
5. <a href="#/economyHats">Economy in Changes</a>
6. <a href="#/policyHats">Policy Problem in Changes</a>
7. <a href="#/multilateralcontest">Multilateral Contest Function</a>
8. <a href="#/milex">Military Expenditure</a>
9. <a href="#/v_est">Protectionism Estimates</a>
10. <a href="#/rcv">Conquest Values</a>
11. <a href="#/chi_est">Estimated Contest Success Probabilities</a>
</div>


```{r, child="slides/appendix.rmd"}
```





# Old

## Coercive International Political Economy {id="cipe"}

- Governments indexed $i \in \left\{ 1, ..., N \right\}$

. . . 

**Sequence**

1. ($\Gamma^{\bm{\tau}}$) Governments make trade policy announcements
2. ($\Gamma^{\bm{a}}$) Wars
    + Winners impose free trade on vanquished governments
3. ($h(\bm{\tau})$) Economic (general equilibrium, @Eaton2002) consequences of trade policies

. . . 

**Payoffs**

$$
G_i \left( h(\bm{\tau}), \bm{a}; \color{bcOrange} v_i \color{black} \right)
$$

- $\color{bcOrange} v_i$ - latent preference for protectionist policies

## Peaceful Equilibrium {id="br"}

\begin{equation*}
\begin{split}
\max_{ \tilde{\bm{\tau}}_i } & \quad G_i \left( h( \tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i} ) \right) \\
\text{subject to} & \quad \underbrace{\tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) G_j \left( h( \bm{1}_i; \tilde{\bm{\tau}}_{-i} ); v_j \right) + \left( 1 - \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \right) G_j \left( h (\tilde{\bm{\tau}} ); v_j \right) - c_j \geq 0}_{\text{war constraint}} \quad \text{for all } j 
\end{split}
\end{equation*}

## Peaceful Equilibrium

\begin{equation*}
\begin{split}
\max_{ \tilde{\bm{\tau}}_i } & \quad G_i \left( h( \tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i} ) \right) \\
\text{subject to} & \quad \color{bcOrange} \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \color{black} G_j \left( h( \bm{1}_i; \tilde{\bm{\tau}}_{-i} ); v_j \right) + \left( 1 - \color{bcOrange} \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \color{black} \right) G_j \left( h (\tilde{\bm{\tau}} ); v_j \right) - c_j \geq 0 \quad \text{for all } j
\end{split}
\end{equation*}

**Contest Function**

$$
\color{bcOrange} \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \color{black} = \frac{ \rho_{ji}(\bm{W}; \bm{\alpha}) M_j }{ \rho_{ji}(\bm{W}; \bm{\alpha}) M_j + M_i }
$$

- $\rho_{ji}(\bm{W}; \bm{\alpha})$ loss of strength gradient
- $M_i$ military strength

## Peaceful Equilibrium

\begin{equation*}
\begin{split}
\max_{ \tilde{\bm{\tau}}_i } & \quad G_i \left( h( \tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i} ) \right) \\
\text{subject to} & \quad \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \color{bcOrange} G_j \left( h( \bm{1}_i; \tilde{\bm{\tau}}_{-i} ); v_j \right) \color{black} + \left( 1 - \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \right) G_j \left( h (\tilde{\bm{\tau}} ); v_j \right) - c_j \geq 0 \quad \text{for all } j
\end{split}
\end{equation*}

**Contest Function**

$$
\tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) = \frac{ \rho_{ji}(\bm{W}; \bm{\alpha}) M_j }{ \rho_{ji}(\bm{W}; \bm{\alpha}) M_j + M_i }
$$

- $\rho_{ji}(\bm{W}; \bm{\alpha})$ loss of strength gradient
- $M_i$ military strength

**Conquest Values**

$$
\color{bcOrange} G_j \left( h( \bm{1}_i; \tilde{\bm{\tau}}_{-i} ); v_j \right)
$$

## Peaceful Equilibrium

\begin{equation*}
\begin{split}
\max_{ \tilde{\bm{\tau}}_i } & \quad G_i \left( h( \tilde{\bm{\tau}}_i; \tilde{\bm{\tau}}_{-i} ) \right) \\
\text{subject to} & \quad \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) G_j \left( h( \bm{1}_i; \tilde{\bm{\tau}}_{-i} ); v_j \right) + \left( 1 - \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \right) G_j \left( h (\tilde{\bm{\tau}} ); v_j \right) - c_j \geq 0 \quad \text{for all } j
\end{split}
\end{equation*}

**Contest Function**

$$
\tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) = \frac{ \rho_{ji}(\bm{W}; \bm{\alpha}) M_j }{ \rho_{ji}(\bm{W}; \bm{\alpha}) M_j + M_i }
$$

- $\rho_{ji}(\bm{W}; \bm{\alpha})$ loss of strength gradient
- $M_i$ military strength

**Conquest Values**

$$
G_j \left( h( \bm{1}_i; \tilde{\bm{\tau}}_{-i} ); v_j \right)
$$

**Equilibrium**

$$
\bm{\tau}^\star(\color{bcOrange} \bm{\theta} \color{black})
$$

- $\color{bcOrange} \bm{\theta} \color{black}$ - estimand

## Estimation {id="estimation"}

**Data**

- $\tau_{ij}$ - aggregate policy barrier to trade imposed by country $i$ on goods from country $j$
  + Measurement: @Cooley2019b

**Measurement Error**

$$
\tau_{ij} = \tau_{ij}^\star(\bm{\theta}) + \epsilon_{ij}
$$

**Mathematical Program with Equilibrium Constraints [@Su2012]**

\begin{equation*}
\begin{split}
\min_{\bm{\theta}, \bm{\tau}^\star} & \quad \sum_i \sum_j \left( \epsilon_{ij}(\bm{\theta}) \right)^2 \\
\text{subject to} & \quad \color{bcOrange} \nabla_{\bm{\tau}_i} \mathcal{L}_i(\bm{\theta}) \color{black} = 0 \quad \text{for all } i
\end{split}
\end{equation*}

- $\color{bcOrange} \nabla_{\bm{\tau}_i} \mathcal{L}_i(\bm{\theta})$ - gradient of Lagrangian

. . . 

**Estimates**

$$
\hat{\bm{\theta}} = \left( \hat{\bm{v}}, \hat{\bm{\alpha}}, \hat{c} \right)
$$

- $\hat{\bm{v}}$ preference for protectionism
- $\hat{\bm{\alpha}}$ loss of military strength over geographic distance
- $\hat{c}$ (relative) costs of war

## Results {id="results"}

**Dyadic War Cost-Benefit Ratios**

```{r cb_ratio, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

# source("02_figs/cbratio.R")
# cb_ratio_plot + theme(aspect.ratio=1)

```











## Thank You {.aligncenter}

[brendancooley.com](http://brendancooley.com)

[bcooley@princeton.edu](mailto:bcooley@princeton.edu)












## ($h(\bm{\tau})$) Economy {id="economy"}

$$
\bm{\tau} = \begin{pmatrix}
\tau_{11} & \cdots & \cdots & \cdots & \tau_{1N} \\
\vdots & \ddots & \vdots & \iddots & \vdots \\
\vdots & \cdots & \tau_{ij} & \cdots & \vdots \\
\vdots & \iddots & \vdots & \ddots & \vdots \\
\tau_{N1} & \cdots & \cdots & \cdots & \tau_{NN}
\end{pmatrix}
$$

## ($h(\bm{\tau})$) Economy

$$
\bm{\tau} = \begin{pmatrix}
\tau_{11} & \cdots & \cdots & \cdots & \tau_{1N} \\
\vdots & \ddots & \vdots & \iddots & \vdots \\
\vdots & \cdots & \color{bcOrange} \tau_{ij} & \cdots & \vdots \\
\vdots & \iddots & \vdots & \ddots & \vdots \\
\tau_{N1} & \cdots & \cdots & \cdots & \tau_{NN}
\end{pmatrix}
$$

<hr style="height:2em; visibility:hidden;" />

- $\color{bcOrange} \tau_{ij}$: trade barrier government $i$ imposes on imports from $j$
- $\color{bcOrange} \tau_{ij} \color{black} - 1$: ad-valorem tariff equivalent
- $\tau_{ij} = 1 \implies$ free trade
- $\tau_{ii} = 1$ for all $i$

## ($h(\bm{\tau})$) Economy

$$
\bm{\tau} = \begin{pmatrix}
\color{bcOrange} \tau_{11} & \color{bcOrange} \cdots & \color{bcOrange} \cdots & \color{bcOrange} \cdots & \color{bcOrange} \tau_{1N} \\
\vdots & \ddots & \vdots & \iddots & \vdots \\
\vdots & \cdots & \tau_{ij} & \cdots & \vdots \\
\vdots & \iddots & \vdots & \ddots & \vdots \\
\tau_{N1} & \cdots & \cdots & \cdots & \tau_{NN}
\end{pmatrix}
$$

<hr style="height:2em; visibility:hidden;" />

$$
\color{bcOrange} \bm{\tau}_1 = \begin{pmatrix} \tau_{11} & \cdots & \cdots & \cdots & \tau_{1N}
\end{pmatrix}
$$

<hr style="height:2em; visibility:hidden;" />

- Government 1's trade policy

## ($h(\bm{\tau})$) Economy

```{r tauhm2, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

source("02_figs/tau.R")
tauhm(tau, highlight="USA")

```

<a href="#/toc" style="float: right;">Back</a>


## ($h(\bm{\tau})$) Economy

$$
\color{bcOrange} \bm{\tau} \color{black} = \begin{pmatrix}
\tau_{11} & \cdots & \cdots & \cdots & \tau_{1N} \\
\vdots & \ddots & \vdots & \iddots & \vdots \\
\vdots & \cdots & \tau_{ij} & \cdots & \vdots \\
\vdots & \iddots & \vdots & \ddots & \vdots \\
\tau_{N1} & \cdots & \cdots & \cdots & \tau_{NN}
\end{pmatrix}
$$

<hr style="height:2em; visibility:hidden;" />

$$
\color{bcOrange} h(\bm{\tau}) \rightarrow \begin{pmatrix}
w_1 \\
\vdots \\
w_N
\end{pmatrix} = \bm{w}
$$

<a href="#/toc" style="float: right;">Back</a>


## Government Objective {id="Gobj"}

$$
h(\bm{\tau}) \rightarrow \begin{pmatrix}
w_1 \\
\vdots \\
w_N
\end{pmatrix} = \color{bcOrange} \bm{w}
$$

<hr style="height:1em; visibility:hidden;" />

- $V_i( \color{bcOrange} \bm{w} \color{black})$: welfare of representative consumer in $i$
- $X_{ij}(\color{bcOrange} \bm{w} \color{black})$: $i$'s imports of goods from $j$
- Rents (tariff revenue):

$$
r_i(\color{bcOrange} \bm{w} \color{black}; v_i) = \sum_j (\tau_{ij} - v_i) X_{ij}(\color{bcOrange} \bm{w} \color{black})
$$

**Government Objective**

$$
G_i = V_i( \color{bcOrange} \bm{w} \color{black}) r_i(\color{bcOrange} \bm{w} \color{black}; v_i)
$$

<a href="#/toc" style="float: right;">Back</a>

## Economy (Consumption) {id="economyA"}

**Consumer's Problem**

\begin{equation*} \label{eq:consumer}
\begin{split}
\max & \quad U_i = Q_i^{\nu_i} S_i^{1 - \nu_i} \\
\text{subject to} & \quad P_i Q_i + P_i^s S_i \leq w_i L_i
\end{split}
\end{equation*}

**CES Preferences over Tradable Varieties**

$$
Q_i = \left( \int_{[0,1]} \alpha_{h(\omega)}^{\frac{1}{\sigma}} q_i(\omega)^{\frac{\sigma - 1}{\sigma}} d \omega \right)^{\frac{\sigma}{\sigma - 1}}
$$

**Tradable Price Index**

$$
P_i = \left( \int_{[0,1]} \alpha_{h(\omega)} p_i(\omega)^{1 - \sigma} d \omega \right)^{\frac{1}{1 - \sigma}}
$$

**Expenditure on Tradables**

$$
E_i^q = \nu_i I_i + D_i = P_i Q_i^\star
$$


## Economy (Production)

**Costs**

\begin{equation} \label{eq:c}
c_i = w_i^{1 - \beta} P_i^{\beta}
\end{equation}

- $w_i$ - cost of labor
- $P_i$ - cost of composite intermediate good
  + equivalent to composite consumption good

$$
E_i^x = \beta X_i
$$

**Local Prices**

$$
p_{ii}(\omega) = \frac{c_i}{z_i(\omega)}
$$

**Technology (Fréchet)**

$$
F_i(z) = \text{Pr} \left\{ z_i(\omega) \leq z \right\} = \exp \left\{ - T_i z^{-\theta} \right\}
$$

## Economy (Equilibrium)

**Total Expenditure on Tradables**

$$
X_i = \underbrace{E_i^q + E_i^x}_{E_i} - D_i
$$

**Trade Shares**

$$
\Omega_{ij}^\star = \left\{ \omega \in [0,1] \left. \right\vert p_{ij}(\omega) \leq \min_{k \neq j} \left\{ p_{ik} \right\} \right\}
$$

$$
\lambda_{ij}(\boldsymbol{w}) = \frac{1}{E_i} \int_{\Omega_{ij}^\star} p_{ij}(\omega) q_i \left( p_{ij} (\omega) \right) d \omega
$$

**Market Clearing**

$$
X_i = \sum_{j=1}^N \lambda_{ji}(\boldsymbol{w}) E_j
$$

<a href="#/toc" style="float: right;">Back</a>

## Economy (Equilibrium in Changes) {id="economyHats"}

$$
\hat{r}_i = \frac{1}{r_i} \left( E_i \hat{E}_i(\hat{\bm{w}}) - \sum_j X_{ij}^{\text{cif}} \hat{X}_{ij}^{\text{cif}}(\hat{\bm{w}}) \right)
$$
$$
\hat{w}_i = \frac{1}{\nu_i w_i L_i} \left( \sum_j \left( (1 - \beta) X_{ji}^{\text{cif}} \hat{X}_{ji}^{\text{cif}}(\hat{\bm{w}}) \right) + (1 - \nu_i) r_i \hat{r}_i(\hat{\bm{w}}) \right)
$$
$$
\hat{E}_i(\hat{\bm{w}}) = \frac{1}{E_i} \left( E_i^q \hat{E}_i^q(\hat{\bm{w}}) + E_i^x \hat{E}_i^x(\hat{\bm{w}}) \right)
$$
$$
\hat{x}_{ij}(\hat{\bm{w}}) = \left( \hat{\tau}_{ij} \hat{w}_j^{1 - \beta} \hat{P}_j(\hat{\bm{w}})^\beta \right)^{-\theta} \hat{P}_i(\hat{\bm{w}})^{\theta}
$$
$$
\hat{P}_i(\hat{\bm{w}}) = \left( \sum_j x_{ij} \left( \hat{\tau}_{ij} \hat{w}_j^{1 - \beta} \hat{P}_j(\hat{\bm{w}})^\beta \right)^{-\theta} \right)^{-\frac{1}{\theta}}
$$
$$
1 = \sum_i y_i \hat{w}_i
$$

<a href="#/toc" style="float: right;">Back</a>

## Policy Problem in Changes {id="policyHats"}

**Government Welfare**

$$
\hat{G}_i(\hat{\bm{\tau}}; v_i) = \hat{V}_i \left( \hat{h}(\hat{\bm{\tau}}) \right) \hat{r}_i \left(\hat{h}(\hat{\bm{\tau}}); v_i \right)
$$

**Constrained Policy Problem in Changes**

\begin{equation*}
\begin{split}
\max_{ \hat{\tilde{\bm{\tau}}}_i } & \quad \hat{G}_i(\hat{\tilde{\bm{\tau}}}_i; \hat{\tilde{\bm{\tau}}}_{-i}) \\
\text{subject to} & \quad \hat{G}_j(\hat{\tilde{\bm{\tau}}}) - \hat{G}_j(\bm{1}_i; \hat{\tilde{\bm{\tau}}}_{-i}) + \hat{c} \left( \tilde{\chi}_{ji}(\bm{Z}; \bm{\theta}) \right)^{-1} \geq 0 \quad \text{for all } j \neq i
\end{split}
\end{equation*}

<a href="#/toc" style="float: right;">Back</a>

## Multilateral Contest Function {id="multilateralcontest"}

$$
\chi_{ij}(\bm{a}, \bm{m}) = \frac{ a_{ij} \rho_{ij}(\bm{W}; \bm{\alpha}) M_i }{ \sum_k a_{kj} \rho_{kj}(\bm{W}; \bm{\alpha}) M_k }
$$

<a href="#/toc" style="float: right;">Back</a>

## Military Expenditure {id="milex"}

```{r milex, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center", fig.height=5}

# source("02_figs/milex.R")
# milexFig + theme(aspect.ratio=1)

```

<a href="#/toc" style="float: right;">Back</a>

## Protectionism Estimates {id="v_est"}


```{r v_estsT, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

# source("02_figs/ccodes.R")

# kable(v_estsT, booktabs = T, caption = "Preference Parameter ($\\tilde{\\bm{v}}$) Estimates", escape = FALSE) %>% kable_styling(position = "center")

```

<a href="#/toc" style="float: right;">Back</a>

## Conquest Values {id="rcv"}

**Conquest Values**

$$
G_j \left( h(\bm{1}_i ; \tilde{\bm{\tau}}_{-i});v_j \right)
$$

```{r rcv, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center"}

# source("02_figs/rcv.R")
# rcvhm(rcv_eq, mint, maxt)

```

<a href="#/toc" style="float: right;">Back</a>

## Probability of Successful Conquest {id="chi_est"}

```{r chi, echo=FALSE, warning=FALSE, message=FALSE,  fig.align="center"}

# source("02_figs/chi.R")
# chihm(chi, minchi, maxchi)

```
<a href="#/toc" style="float: right;">Back</a>


<!-- hide references -->
<hr style="height:30em; visibility:hidden;" />