---
title: "Trade Policy in the Shadow of Power"
subtitle: "Quantifying Military Coercion in the International System"
date: "9 April 2020"
author: Brendan Cooley
position: Ph.D. Candidate
institution: Princeton University
email: "bcooley (at) princeton.edu"
note: These slides available at brendancooley.com/tpsp

bibliography: /Users/brendancooley/Dropbox (Princeton)/References/library.bib
biblio-style: apsr

backgroundTitle: "02_figs/cover.jpg"

output:
  revealjs::revealjs_presentation:
    template: "css/cooley-reveal.html"
    css: "css/cooley-reveal.css"
    backgroundTransition: none
    transition: none
    self_contained: false
    # reveal_plugins: ["notes"]
    lib_dir: index_files
    reveal_options:
      slideNumber: false
      progress: false
      controls: false      
    includes:
      after_body: "css/plugins.html"
---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

code_dir <- "01_code/"
figs_dir <- "02_figs/"
slides_dir <- "slides/"

size = "mid/"

# references from paper
if (file.exists('references.RData')) load('references.RData')

```

```{r, child="slides/introduction.rmd"}
```

# Table of Contents {id="toc"}

<div id="left">
1. <a href="#/introduction">Introduction</a>
2. <a href="#/approach">Approach</a>
3. <a href="#/cipe">Model</a>
4. <a href="#/br">Equilibrium</a>
5. <a href="#/estimation">Estimation</a>
6. <a href="#/results">Results</a>
</div>

<div id="right">
1. <a href="#/economy">Economy (Overview)</a>
2. <a href="#/barriers">Estimated Dyadic Policy Barriers</a>
3. <a href="#/Gobj">Government Objective</a>
4. <a href="#/economyA">Economy (GE)</a>
5. <a href="#/economyHats">Economy in Changes</a>
6. <a href="#/policyHats">Policy Problem in Changes</a>
7. <a href="#/multilateralcontest">Multilateral Contest Function</a>
8. <a href="#/milex">Military Expenditure</a>
9. <a href="#/v_est">Protectionism Estimates</a>
10. <a href="#/rcv">Conquest Values</a>
11. <a href="#/chi_est">Estimated Contest Success Probabilities</a>
</div>


```{r, child="slides/appendix.rmd"}
```

<!-- hide references -->
<hr style="height:30em; visibility:hidden;" />