```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

year <- read_csv(paste0(dataPath, "year.csv"), col_names=FALSE) %>% pull(.)
ccodes <- read_csv(paste0(dataPath, "ccodes.csv"), col_names=FALSE)
y <- read_csv(paste0(dataPath, "y.csv"), col_names=FALSE)

yDF <- bind_cols(ccodes, y)
colnames(yDF) <- c("iso3", "y")

yAll <- sum(yDF$y)
yROW <- yDF %>% filter(iso3=="RoW") %>% pull(y)

```

# Data {id="data"}

Year: `r year`

- $\tau_{ij}$ -- aggregate policy barrier to trade imposed by country $i$ on goods from country $j$
  	+ Measurement: @Cooley2019b (<a href="#/barriers">Barriers</a>)
- $M_i$ -- military expenditure 
	+ SIPRI (<a href="#/milex">Milex</a>)
- $W_{ji}$ -- centroid-centroid distances [@Weidmann2010]

<a href="#/calibration">Economy Calibration ($h(\bm{\tau})$)</a>

- Trade flows
- National accounts (gdp, gross consumption)
- Parameters
	+ share of intermediates in traded goods
	+ share of consumer expenditure spend on traded goods
	+ trade elasticity

## In-Sample Countries

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

source(paste0("../", figs_dir, "ccodes.R"))

```

![](`r paste0(figs_dir, ccodes_table_path)`)

- RoW: Aggregate outside economy (cannot coerce or be coerced)
	+ Non-ROW countriies: `r round( (yAll - yROW) / yAll * 100 )` percent of world GDP.
- EU: Aggregate trade policy and military capacity
	+ Country-level estimation coming soon