```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

use_virtualenv("python3")
c_setup <- import_from_path("c_setup", path=paste0("../", code_dir))
setup <- c_setup$setup("local", size)

ccodes <- read_csv(setup$ccodes_path, col_names=F) %>% pull(.)
Y <- 2011
y <- read_csv(setup$Y_path, col_names=F) %>% pull(.)
tau <- read_csv(setup$tau_path, col_names=F) %>% as.matrix()

yDF <- data.frame(ccodes, y) %>% as_tibble()
colnames(yDF) <- c("iso3", "y")

yAll <- sum(yDF$y)
yROW <- yDF %>% filter(iso3=="RoW") %>% pull(y)

meanTau <- round((mean(tau) - 1) * 100)  # in percent

```

I estimate the model on a set of `r N` governments in the year `r Y`.^[Focusing on a small set of governments is necessary for computational tractability. However, the largest countries (by GDP) are the most attractive targets for coercion, as changes to their trade policies return the largest welfare gains.] These governments are listed in Table \ref{tab:ccodes}. I aggregate all European Union governments into a single entity and collapse all countries not included in the analysis into a "Rest of World" (ROW) aggregate.^[Such an aggregation is necessary in order to calculate fully general equilibrium effects of counterfactual trade policies. However, I prohibit other countries from invading ROW and likewise prohibit ROW from invading others. This ensures that estimates of military parameters depend almost entirely on interactions between countries within my sample.] Non-ROW countries make up `r round( (yAll - yROW) / yAll * 100 )` percent of world GDP.

```{r ccodes, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

source(paste0("../", code_dir, "f_ccodes.R"))
ccodes_table

```

Estimating the model and conducting the subsequent counterfactual exercises require knowledge of governments' trade policies, disaggregated at the directed dyadic level. While detailed data on a particular policy instrument (tariffs) are available to researchers, these are but one barrier governments can use to influence the flow of trade. In a companion paper [@Cooley2019b], I show how to measure aggregate directed trade policy distortions given data on national accounts (gross consumption, gross production, and gross domestic product), price levels, trade flows, and freight costs. This method produces a matrix of trade barriers, in which the $i$, $j$th entry is the magnitude of policy barriers to trade an importing country $i$ imposes on goods from an exporting country $j$. In `r Y`, the estimated barriers were large, equivalent to a `r meanTau` percent import tariff on average.^[These results and the calibration choices that produce this value are discussed in more detail in Appendix `r AeconomyC`.] They also reveal substantial trade policy discrimination, with a subset of developed exporters facing far more favorable market access conditions than their less-developed peer countries. 

I take these estimated trade policies as the equilibrium output of the model developed here. I assume these policies are measured with error and construct an estimator that minimizes the magnitude of the resulting error vector. I sample from bootstrapped iterations of the trade policy estimation routine and re-compute parameter estimates many times in order to construct confidence intervals around my point estimates. 

Estimating the magnitude of these trade policies and tracing their impact government welfare requires specifying a model of the international economy. This model, which follows closely that of @Eaton2002, can be represented succinctly as a mapping $h(\bm{\tau}, \bm{Z}_h; \bm{\theta}_h) = \bm{w}$ where $\bm{\tau}$ is a vector of trade policies, $\bm{Z}_h$ is a vector of economic data (including information on national accounts, price levels, trade flows, and freight costs), and $\bm{\theta}_h$ is a vector of parameters to be calibrated to match empirical analogues. $\bm{w}$ is a vector of wage levels, one for every country, from which equilibrium trade flows and price levels can be calculated. Government welfare is modeled below as a function of the outputs of this economy. I employ the same model of the international economy used to estimate trade policies in @Cooley2019b to calculate the welfare effects of trade policies in this study. The economy, the data required to calibrate it, and the parameter calibration choices I employ are discussed in more detail in Appendix `r AeconomyC`.

In the coercive political economy developed below, governments' relative directed war costs are modeled as a function of the military capability ratio between the attacker and defender, the geographic distance between the belligerents, and the gross domestic product of the attacking country. I store these observable features in the vector $\bm{Z}$. To measure military capability ratios, I employ [SIPRI](https://www.sipri.org/)'s data on military expenditure to measure governments' military capacity. These values are displayed in Figure \ref{fig:milex}. I use data from @Weidmann2010 to calculate centroid-centroid geographic distance between all countries in my sample. Data on gross domestic production comes from the [World Input-Output Database (WIOD)](http://www.wiod.org/home) [@Timmer2015]. 

```{r milex, echo=FALSE, warning=FALSE, message=FALSE, fig.cap = paste("Military expenditure for in-sample governments. Values for ROW and EU are obtained by summing expenditure of all member countries. \\label{fig:milex}"), fig.height=5, dpi=300, fig.pos="t"}

source(paste0("../", code_dir, "f_milex.R"))
milexFig + theme(aspect.ratio=1)

```

## Reduced Form Evidence on Coercion and Trade Policy

To assist in the interpretation of the data, consider a simple bilateral coercive bargaining setting. Governments 1 and 2 bargain over a pie of size 1. Let $x \in [0, 1]$ denote the share of the pie awarded to government 1 (with the remainder, $1-x$, going to government 2). In the trade setting studied here, $x=1$ might correspond to government 1 implementing optimal tariffs and government 2 liberalizing fully. Each government's valuation of the pie is given by an increasing, weakly concave utility function $u_i(x)$. The value of each government's outside option is given by a war function, $w_i(M_i / M_j)$, which depends on their relative military capabilities, $\frac{M_i}{M_j}$. Assume $w_i$ is increasing in this military capability ratio -- that is, more powerful governments enjoy better outside options.

For simplicity, assume the pie is divided via the Nash Bargaining Solution, satisfying
\begin{equation}
\begin{split}
x^\star \in \argmax_x & \quad \left( u_1(x) - w_1(M_1 / M_2) \right) \left( u_2(x) - w_2(M_2 / M_1) \right) \\
\text{subject to} & \quad u_1(x) \geq w_1(M_1 / M_2) \\
& \quad u_2(x) \geq w_2(M_2 / M_1) .
\end{split}
\end{equation}
Taking first order conditions, it is straightforward to show that the allocation to government 1, $x^\star$, satisfies
$$
u_1^\star(x^\star; M_1, M_2) = \frac{u_1^\prime(x^\star)}{u_2^\prime(1 - x^\star)} \left( u_2(1 - x^\star) - w_2(M_2 / M_1) \right) + w_1(M_1 / M_2) . 
$$
Differentiating this equation with respect to government 1's military capacity, $M_1$, we see that $u_1(x^\star; M_1, M_2)$ is increasing in $M_1$,
$$
\frac{\partial u_1^\star(x^\star; M_1, M_2) }{\partial M_1} = \underbrace{- \frac{u_1^\prime(x^\star)}{u_2^\prime(1 - x^\star)} \frac{\partial w_2(M_2 / M_1)}{\partial M_1}}_{>0} + \underbrace{\frac{\partial w_1(M_1 / M_2)}{ \partial M_1}}_{>0} > 0 .
$$
In other words, the distance between government 1's equilibrium utility and the utility it receives at it's ideal point is decreasing in it's relative military advantage.

Suppose that governments endeavor to maximize the welfare of the representative consumer.^[I will relax this assumption in the structural model developed below.] With the economy, $h$, calibrated, I can calculate the change in utility each representative consumer would experience when each other government adopts free trade, relative to their utility at the baseline set of policies. Taking this as a empirical measure of the ratio $u_1^\star(x^\star; M_1, M_2) / u_1(1)$, the model implies this quantity will be increasing in $M_1$, country 1's military capacity. I will refer to this quantity as government 1's inverse *conquest value* vis-à-vis government 2.

```{r rcvm, echo=FALSE, warning=FALSE, message=FALSE, fig.cap = paste0("Correlation between military capability ratios and inverse conquest values, all pairs of in-sample countries. \\label{fig:rcvm}"), fig.height=5, dpi=300, fig.pos="t"}

source(paste0("../", code_dir, "f_tau_rf.R"))
rcvm_plot

```

Figure \ref{fig:rcvm} plots the empirical relationship between military capability ratios and inverse regime change values. A potential "attacking" country's military capability ratio vis a vis every "defending" country is plotted on the x-axis. On the y-axis is the attacking country's value for conquering each defending country. Consistent with the predictions of this simple model, government's inverse conquest values correlate positively with their relative military power. Table \ref{fig:rcvm_reg_table} and Figure \ref{fig:rcvm_reg_dw} display the results of a series of linear models that estimate the conditional correlations between the inverse conquest value and the military capability ratio, distance between the countries, and country-specific constants. 

```{r rcv_reg_table, echo=FALSE, warning=FALSE, message=FALSE, fig.cap = paste0("Conditional correlations between inverse conquest values and military capability ratios, geographic distance, and country-specific constants. \\label{fig:rcvm_reg_tex}"), fig.height=3, dpi=300, fig.pos="t"}

# source(paste0("../", code_dir, "f_tau_rf.R"))
table_tex

```

```{r rcv_reg_dw, echo=FALSE, warning=FALSE, message=FALSE, fig.cap = paste0("\\label{fig:rcvm_reg_dw}"), fig.height=3, fig.width=7, dpi=300, fig.pos="t"}

# source(paste0("../", code_dir, "f_tau_rf.R"))
dw

```

The first model confirms the statistical significance of the correlation shown in Figure \ref{fig:rcvm}. The second model estimates this correlation within potential "attacking" countries. Here, inverse conquest values continue to rise as military advantage rises. The final two models interact the military capability ratio with a measure of distance between the attacker and defender. The estimated correlation between military capbility is not attenuated, but does lose statistical significance in these specifications. Distance and the interaction of distance with military capability does not covary with the inverse conquest values, whether or not country-specific factors are included. These raw correlations are informative about the role of coercion in the formation of trade policy but suggestive at best. Trade policy bargaining is a multilateral endeavor in which third party externalities loom large. Moreover, governments may vary in their preferences for protectionism, changing their ideal policies and their valuations for conquering others. The model developed below accounts explicitly for these features of trade policy bargaining, delivering interpretable estimates of the effects of military capability and geographic distance on trade policy outcomes.






