```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

use_virtualenv("python3")
c_setup <- import_from_path("c_setup", path=paste0("../", code_dir))
setup <- c_setup$setup("local", size)

ccodes <- read_csv(setup$ccodes_path, col_names=F) %>% pull(.)
Y <- 2011
y <- read_csv(setup$Y_path, col_names=F) %>% pull(.)
tau <- read_csv(setup$tau_path, col_names=F) %>% as.matrix()

yDF <- data.frame(ccodes, y) %>% as_tibble()
colnames(yDF) <- c("iso3", "y")

yAll <- sum(yDF$y)
yROW <- yDF %>% filter(iso3=="RoW") %>% pull(y)

meanTau <- round((mean(tau) - 1) * 100)  # in percent

```

I estimate the model on a set of `r N` governments in the year `r Y`.^[Focusing on a small set of governments is necessary for computational tractability. However, the largest countries (by GDP) are the most attractive targets for coercion, as changes to their trade policies return the largest welfare gains.] These governments are listed in Table \ref{tab:ccodes}. I aggregate all European Union governments into a single entity and collapse all countries not included in the analysis into a "Rest of World" (ROW) aggregate.^[Such an aggregation is necessary in order to calculate fully general equilibrium effects of counterfactual trade policies. However, I prohibit other countries from invading ROW and likewise prohibit ROW from invading others. This ensures that estimates of military parameters depend almost entirely on interactions between countries within my sample.] Non-ROW countries make up `r round( (yAll - yROW) / yAll * 100 )` percent of world GDP.

```{r ccodes, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

source(paste0("../", code_dir, "f_ccodes.R"))
ccodes_table

```

Estimating the model and conducting the subsequent counterfactual exercises require knowledge of governments' trade policies, disaggregated at the directed dyadic level. While detailed data on a particular policy instrument (tariffs) are available to researchers, these are but one barrier governments can use to influence the flow of trade. In a companion paper [@Cooley2019b], I show how to measure aggregate directed trade policy distortions given data on national accounts (gross consumption, gross production, and gross domestic product), price levels, trade flows, and freight costs. This method produces a matrix of trade barriers, in which the $i$, $j$th entry is the magnitude of policy barriers to trade an importing country $i$ imposes on goods from an exporting country $j$. In `r Y`, the estimated barriers were large, equivalent to a `r meanTau` percent import tariff on average.^[These results and the calibration choices that produce this value are discussed in more detail in Appendix `r AeconomyC`.] They also reveal substantial trade policy discrimination, with a subset of developed exporters facing far more favorable market access conditions than their less-developed peer countries. 

I take these estimated trade policies as the equilibrium output of the model developed here. I assume these policies are measured with error and construct an estimator that minimizes the magnitude of the resulting error vector. I sample from bootstrapped iterations of the trade policy estimation routine and re-compute parameter estimates many times in order to construct confidence intervals around my point estimates. 

Estimating the magnitude of these trade policies and tracing their impact government welfare requires specifying a model of the international economy. This model, which follows closely that of @Eaton2002, can be represented succinctly as a mapping $h(\bm{\tau}, \bm{Z}_h; \bm{\theta}_h) \rightarrow \bm{w}$ where $\bm{\tau}$ is a vector of trade policies, $\bm{Z}_h$ is a vector of economic data (including information on national accounts, price levels, trade flows, and freight costs), and $\bm{\theta}_h$ is a vector of parameters to be calibrated to match empirical analogues. $\bm{w}$ is a vector of wage levels, one for every country, from which equilibrium trade flows and price levels can be calculated. Government welfare is modeled below as a function of the outputs of this economy. I employ the same model of the international economy used to estimate trade policies in @Cooley2019b to calculate the welfare effects of trade policies in this study. The economy, the data required to calibrate it, and the parameter calibration choices I employ are discussed in more detail in Appendix `r AeconomyC`.

In the coercive political economy developed below, governments' relative directed war costs are modeled as a function of the military capability ratio between the attacker and defender, the geographic distance between the belligerents, and the gross domestic product of the attacking country. I store these observable features in the vector $\bm{Z}$. To measure military capability ratios, I employ [SIPRI](https://www.sipri.org/)'s data on military expenditure to measure governments' military capacity. These values are displayed in Figure \ref{fig:milex}. I use data from @Weidmann2010 to calculate centroid-centroid geographic distance between all countries in my sample. Data on gross domestic production comes from the [World Input-Output Database (WIOD)](http://www.wiod.org/home) [@Timmer2015]. 

```{r milex, echo=FALSE, warning=FALSE, message=FALSE, fig.cap = paste("Military expenditure for in-sample governments. Values for ROW and EU are obtained by summing expenditure of all member countries. \\label{fig:milex}"), fig.height=5, dpi=300, fig.pos="t"}

source(paste0("../", code_dir, "f_milex.R"))
milexFig + theme(aspect.ratio=1)

```

## Reduced Form Evidence on Coercion and Trade Policy

To assist in the interpretation of the following results, consider a simple bilateral coercive bargaining setting. Governments 1 and 2 bargain over a pie of size 1. Let $x \in [0, 1]$ denote the share of the pie awarded to government 1 (with the remainder, $1-x$, going to government 2). Each government's valuation of the pie is given by an increasing, weakly concave utility function $u_i(x)$. The value of each government's outside option is given by a war function, $w_i(M_i / M_j)$, which depends on their relative military capabilities, $\frac{M_i}{M_j}$. Assume $w_i$ is increasing in this military capability ratio -- that is, more powerful governments enjoy better outside options.

For simplicity, assume the pie is divided via the Nash Bargaining Solution, satisfying
\begin{equation}
\begin{split}
x^\star \in \argmax_x & \quad \left( u_1(x) - w_1(M_1 / M_2) \right) \left( u_2(x) - w_2(M_2 / M_1) \right) \\
\text{subject to} & \quad u_1(x) \geq w_1(M_1 / M_2) \\
& \quad u_2(x) \geq w_2(M_2 / M_1) .
\end{split}
\end{equation}
Taking first order conditions, it is straightforward to show that the allocation to government 1, $x^\star$, satisfies
$$
u_1(x^\star; M_1, M_2) = \frac{u_1^\prime(x^\star)}{u_2^\prime(1 - x^\star)} \left( u_2(1 - x^\star) - w_2(M_2 / M_1) \right) + w_1(M_1 / M_2)
$$



