```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

use_virtualenv("python3")
c_setup <- import_from_path("c_setup", path=paste0("../", code_dir))
setup <- c_setup$setup("local", size)

USA_id <- which(ccodes=="USA")
CHN_id <- which(ccodes=="CHN")

source(paste0("../", code_dir, "f_fit.R"))

```

```{r ests, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.cap = paste0("Model parameter estimates and 95 percent confidence intervals. The top panel shows protectionism preference parameter estimates ($v_i$) for each country. The bottom panel shows parameter estimates for observables affecting costs of war ($\\gamma, \\alpha_1, \\alpha_2$). \\label{fig:ests}"), fig.height=5, fig.width=6, dpi=300, fig.pos="t"}

source(paste0("../", code_dir, "f_estimates.R"))

pref_plot / mil_plot + plot_layout(heights=c(2, 1))

```

Figure \ref{fig:ests} displays results from the estimation. Recall that $v_i$ governs the ease with which governments can extract revenues from trade policy distortions. When $v_i$ is higher government $i$ prefers higher barriers to trade, all else equal. When $v_i=1$ the government acts as a classical social welfare maximizer. There is considerable heterogeneity in governments' estimated preferences for protectionism. The United States and Russia are estimated to be relatively liberal, while Australia and Canada are quite protectionist. 

An attacking country's military advantage and g.d.p. are estimated to reduce war costs, facilitating coercion. There are increasing returns to both of these features in reducing the average costs of war ($\gamma, \alpha_2 > 1$). Economically large and military powerful countries are the most effective at coercion, holding the distance of their adversary constant. Figure \ref{fig:war_costs} displays estimated average war costs, relative to those of the United States, holding the distance to the adversary constant. Given its large economy and military, the United States is estimated to enjoy the smallest average war costs. The European Union, China, and Russia pay between `r round(costs$c_mean[costs$iso3=="EU"], 1)` and `r round(costs$c_mean[costs$iso3=="RUS"], 1)` times the costs of the United States to prosecute wars on average. Wars are estimated to cost at least an order of magnitude more than U.S. wars for other countries in the sample.

```{r war_costs, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.cap = paste0("Estimated relative war costs against a fixed adversary. The United States' costs serve as baseline ($c=1$). \\label{fig:war_costs}"), fig.height=4.5, fig.width=4.5, dpi=300, fig.pos="t"}

# source(paste0("../", code_dir, "f_estimates.R"))

costs_plot

```

War costs are estimated to depend on the distance between the attacker and potential adversary. Attackers that are more distant from their adversaries are estimated to enjoy smaller war costs. In other words, model estimates imply an inverse loss of strength gradient. This may emerge due to the peculiarities of military technology in 2011, a period in which geographic distance represents a uniquely small impediment to the projection of force.

The model estimates can be readily transformed to deliver empirical quantities that measure the salience of military coercion in international relations. Figure \ref{fig:rcv} plots the estimated conquest value for each potential attacking country vis-à-vis each potential defending country. These quantities differ from those analyzed in the reduced form section above in that they account explicitly for the attacking government's preferences for protectionism. Russia's conquest values are estimated to be among the highest in the sample. This reflects the relatively poor market access conditions it enjoys at the estimated equilibrium. Because their economies are the largest in the sample, the gains that accrue from successfully conquering the United States, China and the European Union tend to be larger than the gains from conquering other countries. Australia, Canada, and China benefit little from conquering others. This result obtains because of their governments' estimated preferences for protectionism. Conquest stimulates trade that is disadvantageous for a government $i$ when $v_i$ is high and $i$'s trade barriers are lowered below the revenue threshold due to the effects of coercion. This variation in conquest values highlights the dependence of the coercive environment on the underlying international economy and government preferences.

```{r rcv, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.cap = paste0("Estimated conquest value for each potential attacking country vis-à-vis each potential defending country. Darker colors indicate higher conquest values. \\label{fig:rcv}"), fig.height=5, dpi=300, fig.pos="t"}

source(paste0("../", code_dir, "f_rcv.R"))

rcv_hm

```

It is also straightforward to calculate the equilibrium probability of war once the model has been estimated by simply plugging parameter estimates back into the inverse cost distribution given in Equation \ref{eq:inv_costs}.^[These estimated probabilities of war should be interpreted only in relative terms. The overall probability of war is governed by the calibrated parameter $\hat{C}$. Higher values of this parameter would scale down each probability of war but would not shift their relative values.] Figure \ref{fig:pr_peace} plots point estimates and uncertainty intervals surrounding the likelihood of war between all pairs of countries in the sample. In general, governments run very small risks of invasion from other governments. However, the threat of war with the United States looms large in the sample. The probabilities the United States attacks each other country in the sample are highlighted in orange in the Figure. The European Union is also estimated to impose substantial threats.

```{r war_probs, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.cap = paste0("Estimated equilibrium probabilities of war, point estimates and 95 percent confidence intervals. Probabilities the United States attacks each other country highlighted in orange. \\label{fig:pr_peace}"), fig.height=4.5, fig.width=4.5, dpi=300, fig.pos="t"}

source(paste0("../", code_dir, "f_pr_peace.R"))

war_probs_pp

```

It is worth noting that the countries with the highest estimated risk of war with the United States, Japan and Australia, happen to be U.S. allies. The security guarantees encapsulated in these alliances are not explicitly modeled. One way to interpret these results is that Australian and Japanese security would deteriorate rapidly in the absence of U.S. military protection, representing an implicit threat the United States can leverage to affect trade policy.^[@Lake2007 would label these relationships "hierarchical" and based on the authority of the United States to dictate the policy of its subordinates. Still, in Lake's conceptualization, "authority is buttressed by the capacity for coercion" (p. 53).]

## Model Fit and Inferences about Policy Preferences

```{r fit, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.cap = paste0("Correlation between trade barrier data and model predictions. \\label{fig:fit}"), fig.height=4.5, fig.width=4.5, dpi=300, fig.pos="t"}

# source(paste0("../", code_dir, "f_fit.R"))
fit

```

Figure \ref{fig:fit} evaluates the ability of the estimated model to predict the level of trade barriers. The model's mean absolute error is `r round(fit_mae, 2)`, equivalent to a `r round(fit_mae*100, 0)` percent ad valorem tariff. The model's predictions are fairly well correlated with the trade barrier data ($\rho=$ `r round(fit_rho, 2)`). In Appendix `r Afit` I plot the model's predictive error for each directed dyad in the sample, highlighting which observations are well explained by the model and which are not. Of note, Russia faces uniquely poor market access conditions in the data that the model does not fully replicate.

```{r ests_mil_off, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.cap = paste0("Effect of modeling military coercion on inferences about governments' preferences for protectionism. Figure plots point estimates and 95 percent confidence intervals for preference parameters under baseline model and model in which coercion is impossible. \\label{fig:ests_mil_off}"), fig.height=4, fig.width=6, dpi=300, fig.pos="t"}

# source(paste0("../", code_dir, "f_estimates.R"))
pref_plot_mil_off

```

Modeling coercion explicitly both improves model fit and alters inferences about government's underlying preferences for protectionism. I re-estimate the model under the assumption that coercion is impossible. In this model, equilibrium policies reflect only governments' underlying preferences, $v_i$. Estimated preferences for protectionism under this model are shown in Figure \ref{fig:ests_mil_off}. The estimated preferences of militarily powerful countries are largely unchanged across models. This is not true for less powerful countries. The estimated preferences of Australia, Canada, and China move dramatically when coercion is prohibited. The model developed here rationalizes their trade barriers as the result of highly protectionist latent preferences tempered by the effects of international coercion. The coercion-free model instead infers instead that they are relatively liberal in their preferences. Leaving coercion out of the model exerts downward bias on estimates of governments' welfare-mindedness. A large literature employs the equilibrium trade policies of @Grossman1994 or @Grossman1995 to estimate the weight governments place on the welfare of special interests relative to that of society at large [@Goldberg1999; @Mitra2006; @Gawande2009; @Gawande2012; @Ossa2014; @Gawande2015]. Because the "protection for sale" model incorporates no theory of international coercion, these studies over-estimate governments' social welfare consciousness. 

Modeling coercion explicitly also improves model fit substantially. The correlation coefficient between model predictions and observed trade barriers falls to `r round(fit_rho_mo, 2)` when coercion is prohibited. The mean absolute error increases `r round((fit_mae_mo / fit_mae - 1)*100, 1)` percent to `r round(fit_mae_mo, 2)`. In Appendix `r Afit` I replicate Figure \ref{fig:fit} for the coercion-free model. 

