```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

use_virtualenv("python3")
c_setup <- import_from_path("c_setup", path=paste0("../", code_dir))
setup <- c_setup$setup("local", size)

ccodes <- read_csv(setup$ccodes_path, col_names=FALSE)
quantiles_v <- read_csv(setup$quantiles_v_path, col_names=F)

pref_params <- quantiles_v %>% t() %>% as_tibble()
colnames(pref_params) <- c("q025", "q500", "q975")
pref_params$iso3 <- ccodes %>% pull()

v_hat_CHN <- pref_params$q500[pref_params$iso3=="CHN"]
v_hat_USA <- pref_params$q500[pref_params$iso3=="USA"]

source(paste0("../", code_dir, "f_cfct_X.R"))
source(paste0("../", code_dir, "f_pr_peace.R"))

```

## Multipolarity, Trade Policy, and International Trade (I) {id="cfct2"}

```{r, echo=FALSE, warning=FALSE, message=FALSE, dpi=600, fig.align="center", fig.height=5.}

source(paste0("../", code_dir, "f_milex.R"))
milex2030Fig

```

## Multipolarity, Trade Policy, and International Trade (II)

- Value of global trade under multipolarization is `r round(cfct2_trade_ratio*100, 1)` percent its baseline value

```{r, echo=FALSE, warning=FALSE, message=FALSE, dpi=600, fig.align="center", fig.height=4.5}

# source(paste0("../", code_dir, "f_cfct_tau.R"))
tau_pp_china

```

<a href="#/cfct_main">Back</a>

## Chinese Preference Liberalization and the Risk of War {id="cfct3"}

- $\hat{v}_{\text{CHN}}=$ `r round(v_hat_CHN, 2)`, $v_{\text{CHN}}^\prime=$ `r round(v_hat_USA, 2)`
- Reduces probability of U.S.-China war from `r round(pw_USA*100, 1)` percent to `r round(pw4_USA*100, 1)` percent

```{r, echo=FALSE, warning=FALSE, message=FALSE, dpi=600, fig.align="center", fig.height=4.}

# source(paste0("../", code_dir, "f_cfct_tau.R"))
war_probs_pp4

```

<a href="#/cfct_main">Back</a>