```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

use_virtualenv("python3")
c_setup <- import_from_path("c_setup", path=paste0("../", code_dir))
setup <- c_setup$setup("local", size)

```

## Counterfactuals (Overview) {id="cfct_main"}

**Counterfactual Policies** $\tilde{\bm{\tau}}^\star(\bm{\theta}_m^\prime; \bm{Z}_m^\prime)$

- $\bm{\theta}_m^\prime$ -- counterfactual parameters (e.g. preferences)
- $\bm{Z}_m^\prime$ -- counterfactual data (e.g. military expenditure)

. . .

**Economic Effects of Counterfactual Policies**

$$
h \left( \tilde{\bm{\tau}}^\star(\bm{\theta}_m^\prime; \bm{Z}_m^\prime) \right)
$$

. . .

**Scenarios**

1. A Coercion-Free World
2. <a href="#/cfct2">Multipolarity, Trade Policy, and International Trade</a>
3. <a href="#/cfct3">Chinese Preference Liberalization and the Risk of War</a>

## Coercion-Free World: Policies

```{r, echo=FALSE, warning=FALSE, message=FALSE, dpi=600, fig.align="center", fig.height=5.}

source(paste0("../", code_dir, "f_cfct_X.R"))
source(paste0("../", code_dir, "f_cfct_tau.R"))
tau_pp_demilitarization_base

```

## Coercion-Free World: Policies

```{r, echo=FALSE, warning=FALSE, message=FALSE, dpi=600, fig.align="center", fig.height=5.}

source(paste0("../", code_dir, "f_cfct_X.R"))
source(paste0("../", code_dir, "f_cfct_tau.R"))
tau_pp_demilitarization

```

## Coercion-Free World: Trade

- Moving from pacifism to 2011 military expenditure levels $\rightarrow$ `r round(((cfct1_trade_ratio**-1)-1)*100, 1)` percent increase in value of world trade

```{r, echo=FALSE, warning=FALSE, message=FALSE, dpi=600, fig.align="center", fig.height=4.5}

# source(paste0("../", code_dir, "f_cfct_X.R"))
# source(paste0("../", code_dir, "f_cfct_tau.R"))
X_diff_pp_dm1

```

## Coercion-Free World: Trade

- Moving from pacifism to 2011 military expenditure levels $\rightarrow$ `r round(((cfct1_trade_ratio**-1)-1)*100, 1)` percent increase in value of world trade

```{r, echo=FALSE, warning=FALSE, message=FALSE, dpi=600, fig.align="center", fig.height=4.5}

# source(paste0("../", code_dir, "f_cfct_X.R"))
# source(paste0("../", code_dir, "f_cfct_tau.R"))
X_diff_pp_dm2

```

## Coercion-Free World: Welfare


```{r, echo=FALSE, warning=FALSE, message=FALSE, dpi=600, fig.align="center", fig.height=5.}

source(paste0("../", code_dir, "f_cfct_welfare.R"))
deltaG1 + deltaU1

```
