```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

yDF <- bind_cols(ccodes, y)
colnames(yDF) <- c("iso3", "y")

yAll <- sum(yDF$y)
yROW <- yDF %>% filter(iso3=="ROW") %>% pull(y)

```

I estimate the model on a set of `r N` governments in the year `r Y`.^[Focusing on a small set of governments is necessary for computational tractability. However, the largest countries (by GDP) are the most attractive targets for coercion, as changes to their trade policies return the largest welfare gains, regardless of whether the coercer is a rent-maximizer or welfare-maximizer. The estimated model is therefore more useful in understanding "great power politics," rather than smaller political-economic conflicts of interest.] These governments are listed in Table \ref{tab:ccodes}. I aggregate all European Union governments into a single entity and collapse all countries not included in the analysis into a "Rest of World" (ROW) aggregate.^[Such an aggregation is necessary in order to calculate fully general equilibrium effects of counterfactual trade policies. However, I prohibit other countries from invading ROW and likewise prohibit ROW from invading others. This ensures that estimates of military parameters depend almost entirely on interactions between countries within my sample.] Non-ROW countries make up `r round( (yAll - yROW) / yAll * 100 )` percent of world GDP.

```{r ccodes, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

# source("../02_figs/ccodes.R")

# kable(ccodesT, "latex", booktabs = T, caption = "In-Sample Countries \\label{tab:ccodes}") %>% kable_styling(position = "center")

```

Solving the economy in changes for a set of $\hat{\bm{\tau}}$ requires values for a vector of economic parameters $\bm{\theta}_h$ and data on trade flows, policy barriers, and and national accounts. I discuss how I calibrate the economy and the data sources used to do so in Appendix `r AeconomyC`. There, I also report the magnitude of policy barrier estimates $\tilde{\bm{\tau}}$ from @Cooley2019b. With $\hat{h}(\hat{\bm{\tau}}; \bm{\theta}_h)$ calibrated, $\hat{G}_i(\hat{\bm{\tau}})$ can be calculated for any set of trade policies and the optimal policy change problem (\ref{eq:optTaujHat}) can be solved, yielding $\hat{\bm{\tau}}_i^{j \star}$ for all $i, j$.

With the economy calibrated and policy barrier estimates in hand, I require only a measure of each government's military endowment ($M_i$) and data on dyadic geography ($\bm{W}$). I use [SIPRI](https://www.sipri.org/)'s data on military expenditure to measure governments' military capacity. These values are displayed in Figure \ref{fig:milex}.

```{r milex, echo=FALSE, warning=FALSE, message=FALSE, fig.cap = paste("Military expenditure for in-sample governments. Values for ROW and EU are obtained by summing expenditure of all member countries. \\label{fig:milex}"), fig.height=5, dpi=300, fig.pos="t"}

source("../02_figs/milex.R")
milexFig + theme(aspect.ratio=1)

```

Finally, I use data from @Weidmann2010 to calculate centroid-centroid geographic distance between all countries in my sample. I take the natural log of this value to be the only variable affecting power projection capacity in $\bm{W}$. 