```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

# rcv0max <- max(rcv0)
# coords <- which(rcv0 == max(rcv0), arr.ind = TRUE)

# ccodesL <- ccodes %>% pull(.)

# rcv0j <- ccodesL[coords[1]]
# rcv0i <- ccodesL[coords[2]]

# rcv0jName <- ccodesT %>% filter(iso3==rcv0j) %>% pull(`Country Name`)
# rcv0iName <- ccodesT %>% filter(iso3==rcv0i) %>% pull(`Country Name`)
USA_id <- which(ccodes=="USA")
CHN_id <- which(ccodes=="CHN")

chi_gamma_ex <- 2^gamma_tilde / (2^gamma_tilde + 1)
rho_ex = exp(-1*alpha_tilde*log(W[USA_id, CHN_id] %>% pull(.)))

```

*NOTE: Computing uncertainty intervals is computationally expensive and in-progress. I report and discuss point estimates here, with the necessary caution such preliminary discussion requires.*

Estimates of preference weights are reported in Table \ref{tab:b_estsT}. In @Cooley2019b, I show that developed countries tend to adopt higher trade barriers than their developing peers. Consistent with this finding, the European Union and Japan are assessed to have high values of $b_i$.


```{r b_estsT, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

source("../02_figs/ccodes.R")

kable(b_estsT, "latex", booktabs = T, caption = "Preference Parameter ($\\tilde{\\bm{b}}$) Estimates \\label{tab:b_estsT}", escape = FALSE) %>% kable_styling(position = "center")

```

With estimates of $b_i$ in hand, I can calculate each government's conquest value vis-à-vis all other governments. Recall that $\hat{\bm{\tau}}_i^{j \star}$ is the set of policies government $j$ would impose on $i$ if it successfully prosecuted a war against the latter. Then, $j$'s counterfactual utility in this scenario can be readily calculated given knowledge of its objective function (\ref{eq:Ghat}). These values are shown in Figure \ref{fig:rcv}. Each cell measures the utility change each row government experiences when successfully conquering each column government. Darker colors correspond to larger changes in utility.

Governments that face poor market access conditions and/or are rent-maximizing gain the most from successful wars, relative to the status quo. When they win wars, rent-maximizing governments impose policies designed to direct trade into their borders. As imports go up, revenue collection potential also increases. The value of war is lower for welfare-maximizing governments. Still, welfare-maximizing governments facing poor market access benefit substantially from winning wars against countries with large markets and high barriers to trade. In the model, peace requires that the probabilistic benefits of war do not exceed war's cost for each directed pair of governments. These values assist in the identification of the power projection and preference parameters in $\bm{\theta}_m$.

```{r rcv_b, echo=FALSE, warning=FALSE, message=FALSE, fig.cap = paste0("Conquest values evaluated at $\\tilde{\\bm{b}}$. Each cell corresponds to the change in utility an attacking country (row) receives for successfully invading the each defending country (column). Darker values correspond to higher utility changes. \\label{fig:rcv}"), fig.height=4, dpi=300, fig.pos="t"}

source("../02_figs/rcv.R")
rcvhm(rcv_b, mint, maxt)

```

Turning to these parameters, I estimate $\gamma$ to be `r round(gamma_tilde, 2)`. This is consistent with a positive effect of military advantage on counterfactual war outcomes, holding power projection capacity constant. In particular, a 2:1 advantage in military spending translates into a `r round(chi_gamma_ex * 100, 1)` percent chance of winning a war, assuming no strength is lost due to the loss of strength gradient ($\rho_{ji} = 1$). 

Governments also face significant obstacles to projecting power. I estimate $\alpha$ to be `r round(alpha_tilde, 2)`. At this value, if the United States wished to invade China, its effective strength would decline by a factor of `r round(1 / rho_ex, 1)` due to the distance between the countries. 

Figure \ref{fig:chi} combines these estimates to produce estimates of the contest function $\tilde{\chi}_{ji}$ for each pair of countries. The United States' military advantage is reflected in its higher probability of success in conquest. However, conquest is estimated to be a difficult endeavor in modern international relations -- no country has a better than even chance of conquering another country within the sample.

```{r chi, echo=FALSE, warning=FALSE, message=FALSE, fig.cap = paste0("Estimated probability of successful conquest for each attacking country (row) in war against every defending country (column). Each probability is reported in the appropriate cell of the heatmap. \\label{fig:chi}"), fig.height=4, dpi=300, fig.pos="t"}

source("../02_figs/chi.R")
chihm(chi, minchi, maxchi)

```