```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

# rcv0max <- max(rcv0)
# coords <- which(rcv0 == max(rcv0), arr.ind = TRUE)

# ccodesL <- ccodes %>% pull(.)

# rcv0j <- ccodesL[coords[1]]
# rcv0i <- ccodesL[coords[2]]

# rcv0jName <- ccodesT %>% filter(iso3==rcv0j) %>% pull(`Country Name`)
# rcv0iName <- ccodesT %>% filter(iso3==rcv0i) %>% pull(`Country Name`)
USA_id <- which(ccodes=="USA")
CHN_id <- which(ccodes=="CHN")

# chi_gamma_ex <- 2^gamma_tilde / (2^gamma_tilde + 1)
rho_ex = exp(-1*alpha1*log(W[USA_id, CHN_id] %>% pull(.)))

```

*NOTE: Computing uncertainty intervals is computationally expensive and in-progress. I report and discuss point estimates here, with the necessary caution such preliminary discussion requires.*

Estimates of preference weights are reported in Table \ref{tab:v_estsT}. In @Cooley2019b, I show that developed countries tend to adopt higher trade barriers than their developing peers. Consistent with this finding, the European Union and Japan are assessed to have high values of $v_i$.


```{r v_estsT, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

source("../02_figs/ccodes.R")

kable(v_estsT, "latex", booktabs = T, caption = "Preference Parameter ($\\tilde{\\bm{v}}$) Estimates \\label{tab:b_estsT}", escape = FALSE) %>% kable_styling(position = "center")

```

With estimates of $v_i$ in hand, I can calculate each government's conquest value vis-à-vis all other governments. Recall that governments impose free trade on other governments when they defeat them in wars. Then, $j$'s counterfactual utility in this scenario can be readily calculated given knowledge of its objective function (\ref{eq:Ghat}). These values are shown in Figure \ref{fig:rcv}. Each cell measures the utility change each row government experiences when successfully conquering each column government. Darker colors correspond to larger changes in utility.

Governments that face poor market access conditions gain the most from successful wars, relative to the status quo. In the model, peace requires that the probabilistic benefits of war do not exceed war's cost for each directed pair of governments. These conquest values assist in the identification of the power projection and war cost parameters in $\bm{\theta}_m$.

```{r rcv, echo=FALSE, warning=FALSE, message=FALSE, fig.cap = paste0("Conquest values evaluated at $\\tilde{\\bm{b}}$. Each cell corresponds to the change in utility an attacking country (row) receives for successfully invading the each defending country (column). Darker values correspond to higher utility changes. \\label{fig:rcv}"), fig.height=4, dpi=300, fig.pos="t"}

source("../02_figs/rcv.R")
rcvhm(rcv_eq, mint, maxt)

```

Governments also do not face obstacles to projecting power over space. I estimate $\alpha$ to be `r round(alpha1, 5)`. At this value, if the United States wished to invade China, its effective strength would *increase* by a factor of `r round(rho_ex, 1)` due to the distance between the countries. 

Figure \ref{fig:chi} combines these estimates to produce estimates of the contest function $\tilde{\chi}_{ji}$ for each pair of countries. The United States' military advantage is reflected in its higher probability of success in conquest.

```{r chi, echo=FALSE, warning=FALSE, message=FALSE, fig.cap = paste0("Estimated probability of successful conquest for each attacking country (row) in war against every defending country (column). Each probability is reported in the appropriate cell of the heatmap. \\label{fig:chi}"), fig.height=4, dpi=300, fig.pos="t"}

source("../02_figs/chi.R")
chihm(chi, minchi, maxchi)

```

While governments do not face a geographic loss of strength gradient, wars are still costly. I estimate $\hat{c}$ to be `r round(c_hat, 2)`. Dividing this value by governments' conquest values, shown in Figure \ref{fig:rcv}, I compute war's cost benefit ratio to be `r round(cb_ratio_mean, 2)` on average. 